---
title: "How to be Curious instead of Contrarian About Covid 19 Part 2: Cases, Tests, and Deaths"
output:
  html_notebook:
    toc: yes
date: 
author: 
affiliation: Director, Machine Learning for Social Science Lab, Center for Peace and Security Studies, University of California San Diego
editor_options: 
  chunk_output_type: inline
---

Rex W. Douglass

<style type="text/css">
blockquote {
    padding: 10px 20px;
    margin: 0 0 20px;
    font-size: 14px;
    border-left: 5px solid #eee;
}
</style>

The good news brigade is back at it, looking for angles with which to interpret count data that support a happy or underdog story.

```{r}
#libraries
library(lubridate)
library(tidyverse)

#devtools::install_github("ropensci/USAboundaries")
#devtools::install_github("ropensci/USAboundariesData")
library(USAboundaries) ; #install.packages('USAboundaries')
data(state_codes)

library(tidyverse)
library(scales)
library(gghighlight)
library(lubridate)
library(R0)  # consider moving all library commands to top -- this one was in a loop below

library(WikidataR)
library(countrycode)

library(usmap) ; # install.packages('usmap')
data(statepop)
#devtools::install_github("ropensci/USAboundaries")
#devtools::install_github("ropensci/USAboundariesData")
library(USAboundaries) ; #install.packages('USAboundaries')
data(state_codes)

library(tidyverse)
library(sf)

```




Country codes

```{r}

library(countrycode)
exclude <- c("ar5", "continent", "country.name.de.regex", "country.name.en.regex", "eurocontrol_pru", "eurocontrol_statfor", "icao.region", "region",
             "cldr.variant.ccp","cldr.variant.dz", "cldr.variant.ce", "cldr.variant.brx","cldr.variant.bn_in","cldr.variant.bn","cldr.variant.fa","cldr.variant.fa_af", "cldr.variant.ja","cldr.variant.ka",
             "cldr.variant.kk","cldr.variant.km","cldr.variant.kn","cldr.variant.ko","cldr.variant.ko_kp","cldr.variant.kok","cldr.variant.ks","cldr.variant.lo","cldr.variant.my","cldr.variant.mzn","cldr.variant.ne",
             "cldr.variant.or","cldr.variant.pa","cldr.variant.ps","cldr.variant.sd","cldr.variant.shi","cldr.variant.si","cldr.variant.sr","cldr.variant.sr_cyrl_ba","cldr.variant.sr_cyrl_me","cldr.variant.sr_cyrl_xk","cldr.variant.ta",
             "cldr.variant.te","cldr.variant.th","cldr.variant.ti","cldr.variant.ug","cldr.variant.uk","cldr.variant.ur","cldr.variant.ur_in","cldr.variant.uz_cyrl","cldr.variant.vai","cldr.variant.yi","cldr.variant.yo","cldr.variant.yo_bj",
             "cldr.variant.yue","cldr.variant.yue_hans","cldr.variant.zgh","cldr.variant.zh","cldr.variant.zh_hant","cldr.variant.zh_hant_hk",
             "un.name.ar","un.name.ru","un.name.zh","cldr.name.am","cldr.name.ar","cldr.name.ar_ly","cldr.name.ar_sa","cldr.name.as","cldr.name.az","cldr.name.az_cyrl",
             "cldr.name.be","cldr.name.bg","cldr.name.bm","cldr.name.bn","cldr.name.brx","cldr.name.bs_cyrl","cldr.name.ccp","cldr.name.ce","cldr.name.chr","cldr.name.chr","cldr.name.ckb","cldr.name.dz","cldr.name.el",
             "cldr.name.fa","cldr.name.fa_af","cldr.name.gu","cldr.name.he","cldr.name.hi","cldr.name.hy","cldr.name.ja","cldr.name.ka","cldr.name.km","cldr.name.kn","cldr.name.ko",
             "cldr.short.yo_bj"  ,    "cldr.name.tk"         , "cldr.short.tk"        , "cldr.variant.tk"      , "cldr.name.mgh"     ,    "cldr.short.mgh"     ,   "cldr.variant.mgh"      ,"cldr.short.el"        , "cldr.variant.el"   ,    "cldr.name.mk"    ,     
             "cldr.name.sr"     ,     "cldr.name.sr_cyrl_ba" , "cldr.name.sr_cyrl_me" , "cldr.name.sr_cyrl_xk" , "cldr.short.mk"    ,     "cldr.short.sr"      ,   "cldr.short.sr_cyrl_ba", "cldr.short.sr_cyrl_me", "cldr.short.sr_cyrl_xk", "cldr.variant.mk"      ,
             "cldr.name.kk"     ,     "cldr.short.kk"        , "cldr.name.ky"     ,     "cldr.name.mn"         , "cldr.name.ru"     ,     "cldr.name.ru_ua"    ,   "cldr.short.bg"        , "cldr.short.bs_cyrl" ,   "cldr.short.ky"   ,      "cldr.short.mn"       , 
             "cldr.short.ru"     ,    "cldr.short.ru_ua"     , "cldr.variant.bg"  ,     "cldr.variant.bs_cyrl" , "cldr.variant.ky"   ,    "cldr.variant.mn"    ,   "cldr.variant.ru"      , "cldr.variant.ru_ua" ,   "cldr.name.uk"    ,      "cldr.short.be"       , 
             "cldr.short.uk"      ,   "cldr.variant.be"      , "cldr.name.tg"     ,     "cldr.name.uz_cyrl"  ,   "cldr.short.tg"      ,   "cldr.short.uz_cyrl" ,   "cldr.variant.tg"      , "cldr.name.tt"       ,   "cldr.short.tt"   ,      "cldr.variant.tt"     , 
             "cldr.short.az_cyrl"  ,  "cldr.variant.az_cyrl" , "cldr.short.ce"    ,     "cldr.short.ka"      ,   "cldr.short.hy"       ,  "cldr.variant.hy"    ,   "cldr.name.yi"         , "cldr.short.yi"      ,   "cldr.short.he"   ,      "cldr.variant.he"     , 
             "cldr.short.ar"       ,  "cldr.short.ar_ly"   ,   "cldr.short.ar_sa" ,     "cldr.variant.ar"    ,   "cldr.variant.ar_ae" ,   "cldr.variant.ar_ly" ,   "cldr.variant.ar_sa"   , "cldr.name.ug"       ,   "cldr.short.ug"   ,      "cldr.short.ckb"     ,  
             "cldr.variant.ckb"   ,   "cldr.name.ps"       ,   "cldr.name.sd"     ,     "cldr.name.ur"       ,   "cldr.name.ur_in"    ,   "cldr.name.uz_arab"  ,   "cldr.short.fa"        , "cldr.short.fa_af"   ,   "cldr.short.ps"    ,     "cldr.short.sd"     ,   
             "cldr.short.ur"      ,   "cldr.short.ur_in"   ,   "cldr.name.ks"     ,     "cldr.short.ks"      ,   "cldr.name.mzn"      ,   "cldr.short.mzn"     ,   "cldr.name.shi"        , "cldr.name.zgh"      ,   "cldr.short.shi"   ,     "cldr.short.zgh"    ,   
             "cldr.name.ti"       ,   "cldr.short.am"      ,   "cldr.short.ti"    ,     "cldr.variant.am"    ,   "cldr.name.mr"       ,   "cldr.short.mr"      ,   "cldr.variant.mr"      , "cldr.name.kok"      ,   "cldr.name.ne"      ,    "cldr.short.kok"     ,  
             "cldr.short.ne"      ,   "cldr.short.hi"      ,   "cldr.variant.hi"  ,     "cldr.short.brx"     ,   "cldr.short.as"      ,   "cldr.short.bn"      ,   "cldr.variant.as"      , "cldr.name.pa"       ,   "cldr.short.pa"      ,   "cldr.short.gu"     ,   
             "cldr.variant.gu"    ,   "cldr.name.or"       ,   "cldr.short.or"    ,     "cldr.name.ta"       ,   "cldr.short.ta"      ,   "cldr.name.te"       ,   "cldr.short.te"        , "cldr.short.kn"      ,   "cldr.name.ml"        ,  "cldr.short.ml"    ,    
             "cldr.variant.ml"    ,   "cldr.name.si"       ,   "cldr.short.si"    ,     "cldr.name.th"       ,   "cldr.short.th"      ,   "cldr.name.lo"       ,   "cldr.short.lo"        , "cldr.short.dz"      ,   "cldr.name.my"       ,   "cldr.short.my"    ,    
             "cldr.short.ccp"     ,   "cldr.short.km"      ,   "cldr.short.chr"   ,     "cldr.variant.chr"   ,   "cldr.name.vai"       ,  "cldr.short.vai"     ,   "cldr.name.ko_kp"      , "cldr.short.ko"      ,   "cldr.short.ko_kp"    ,  "cldr.short.ja"    ,    
             "cldr.name.yue"      ,   "cldr.name.yue_hans" ,   "cldr.name.zh"     ,     "cldr.name.zh_hant"  ,   "cldr.name.zh_hant_hk" , "cldr.short.yue"     ,   "cldr.short.yue_hans"  , "cldr.short.zh"      ,   "cldr.short.zh_hant"  ,  "cldr.short.zh_hant_hk"
             )
length(names(codelist))
vars <- setdiff(names(codelist),exclude)
length(vars) #489
codelist_t <- t(codelist[,vars])

sort(codelist_t[,1])

countries_list <- list()
for(q in vars){
  print(q)
  temp <- countries
  temp$name <- countrycode(
    sourcevar=countries$name,
    origin="country.name",
    destination=q,
    warn = F,
    nomatch = NA,
    custom_dict = NULL,
    custom_match = NULL,
    origin_regex = FALSE
  )
  if(!is.numeric(temp$name)) { #auto exclude those columns that are numeric codes
    countries_list[[q]] <- temp
  }
}

countries_df <- bind_rows(countries_list)
dim(countries_df) #122,368

rex_clean <- function(x){ x %>% stri_trans_general("latin-ascii") %>% stri_replace_all(regex="[^A-Za-z0-9]","") %>% tolower() } #so individually, each string should be devoid of spaces,noncharacters, and nonlatin

countries_df_unique <- countries_df %>% 
                       mutate(name= name %>% rex_clean()   ) %>%
                       distinct() %>% 
                       filter(!is.na(name)) %>% 
                       add_count(name) %>% filter(n==1) %>% dplyr::select(-n) %>%
                       filter(is.na(as.numeric(name)))
dim(countries_df_unique) #13,653

countries_df_unique <- bind_rows(
  gadm36_df %>% dplyr::select(gid=GID_0, name=NAME_0 ) %>% mutate(name= name %>% rex_clean()   ),
  countries_df_unique
) %>% distinct()


```

GADM

Turns out it's not a panacea. Catches a whole lot but fails like on Delhi's second level administrative boundaries for some reason. Alternate names get poorer for some parts of the world. Also really hit or miss coverage on cities.

```{r}

if(fromscratch){

  gadm36 = st_read("/media/skynet2/905884f0-7546-4273-9061-12a790830beb/rwd_github_private/NESSgadm/data_in/gadm36_gpkg/gadm36.gpkg")
  
  gadm36_df <- gadm36 %>% as.data.frame()
  
  countries <- gadm36_df %>% dplyr::select(gid=GID_0, name=NAME_0 ) %>% distinct()
  
  #Gadm is good about aliases for lower level entities but not countries so use countrycode to grab a bunch of other ways to write countries
  #For variety, we're going to throw in all the country aliases in countrycode


  
  temp1 <- bind_rows(
    countries_df_unique,
    gadm36_df %>% dplyr::select(gid=GID_1, name=NAME_1 , varname=VARNAME_1, type=TYPE_1, engtype=ENGTYPE_1, validfrom=VALIDFR_1, validto=VALIDTO_1 ) %>% distinct(),
    gadm36_df %>% dplyr::select(gid=GID_2, name=NAME_2 , varname=VARNAME_2, type=TYPE_2, engtype=ENGTYPE_2, validfrom=VALIDFR_2, validto=VALIDTO_2 ) %>% distinct(),
    gadm36_df %>% dplyr::select(gid=GID_3, name=NAME_3 , varname=VARNAME_3, type=TYPE_3, engtype=ENGTYPE_3, validfrom=VALIDFR_3, validto=VALIDTO_3 ) %>% distinct(),
    gadm36_df %>% dplyr::select(gid=GID_4, name=NAME_4 , varname=VARNAME_4, type=TYPE_4, engtype=ENGTYPE_4, validfrom=VALIDFR_4, validto=VALIDTO_4 )
  ) %>% distinct()
  dim(temp1)
  
  temp2 <- bind_rows(
    temp1 %>% dplyr::select(gid, name=name , type, engtype, validfrom, validto ),
    temp1 %>% dplyr::select(gid, name=varname , type, engtype, validfrom, validto )
  )  %>%
    distinct() %>% 
    separate_rows(name,sep="\\|") %>%
    mutate(name = trimws(name)) %>%
    filter(!is.na(name) & name!='') %>%
    distinct() 
  
  temp3 <- bind_rows(
    temp2 %>% dplyr::select(gid, name , type=type, validfrom, validto ),
    temp2 %>% dplyr::select(gid, name , type=engtype, validfrom, validto )
  )  %>%
    distinct() %>% 
    separate_rows(type,sep="\\|") %>%
    mutate(type = trimws(type)) %>%
    distinct() 
  dim(temp3)
  #Territorio Nacional|Provincia
  
  temp4 <- bind_rows(
    temp3 %>% dplyr::select(gid, name , validfrom, validto ), #just the name
    temp3 %>% filter(!is.na(type) & type!='') %>% mutate(name=paste0(name," ",type)) %>% dplyr::select(gid, name , validfrom, validto ), #original name followed by the type that it is
    temp3 %>% filter(!is.na(type) & type!='') %>% mutate(name=paste0(type," of ",name)) %>% dplyr::select(gid, name , validfrom, validto ), #type followed by of, so state of, county of province of, etc.
  )  %>%
    distinct() %>% 
    mutate(name = trimws(name)) %>%
    distinct() 
  dim(temp4) #1,657,967 #1019451
  
  #dates
  dates_df <- temp4 %>% dplyr::select(gid,validfrom, validto) %>% distinct()

  library(data.table)
  temp5 <- temp4 %>% dplyr::select(gid,name) %>% as.data.table()

  library(dtplyr) #install.packages("dtplyr")
  library(stringi)
  rex_clean <- function(x){ x %>% stri_trans_general("latin-ascii") %>% stri_replace_all(regex="[^A-Za-z0-9]","") %>% tolower() } #so individually, each string should be devoid of spaces,noncharacters, and nonlatin
  temp5[,name:=rex_clean(name),]
  temp5 <- temp5 %>% distinct()
  dim(temp5) 
  
  #but between levels we'll put an underscore. Number of udnerscores tells you how many levels down it is
  #we do this better above so we're more interested in level1 below
  level0 <- countries_df_unique %>% mutate(name=rex_clean(name)) %>% distinct() %>% arrange(gid) %>% filter(!is.na(name) & name!='') %>% filter(!duplicated(name))
  dim(level0) #
  
  #temp <- level0 %>% count(name)
  
  gadm1 <- gadm36_df %>% dplyr::select(gid=GID_1, a=GID_0, b=GID_1) %>% filter(!is.na(a) & !is.na(b)) %>% 
            #left_join(temp5 %>% dplyr::select(a=gid, name_a=name) %>% filter(!is.na(a) & !is.na(name_a) & name_a!='')  ) %>% 
            left_join(temp5 %>% dplyr::select(b=gid, name_b=name) %>% filter(!is.na(b) & !is.na(name_b) & name_b!='')  ) %>% dplyr::select(gid0=a, gid1=b, name1=name_b)  %>% distinct() 
            #mutate(name=paste0(name_a,"_",name_b)) %>% dplyr::select(gid, name) %>% distinct() %>% filter(!is.na(name) & name!='') #%>% filter(!duplicated(name))
  dim(gadm1) #31362
  #level1_distinct <- level1 %>% distinct() #no dupes
  
  #need to redo 2 through whatever below like gadm1 here
  gadm2 <- gadm36_df %>% dplyr::select(gid=GID_2, a=GID_0, b=GID_1, c=GID_2) %>% filter(!is.na(a) & !is.na(b) & !is.na(c)) %>% 
            #left_join(temp5 %>% dplyr::select(a=gid, name_a=name) %>% filter(!is.na(a) & !is.na(name_a) & name_a!='')  ) %>% 
            left_join(temp5 %>% dplyr::select(c=gid, name=name) %>% filter(!is.na(c) & !is.na(name) & name!='')  ) %>% dplyr::select(gid0=a, gid1=b, gid2=c,  name2=name)  %>% distinct() 
            #mutate(name=paste0(name_a,"_",name_b)) %>% dplyr::select(gid, name) %>% distinct() %>% filter(!is.na(name) & name!='') #%>% filter(!duplicated(name))
  dim(gadm2) #438,130
    

  
  library(fst)
  write_fst( level0to3, '/media/skynet2/905884f0-7546-4273-9061-12a790830beb/rwd_github_private/NESScovid19/data_temp/level0to3.fst', compress = 100) #upping the compression hoping it speeds up the read
  level0to3 <- read_fst('/media/skynet2/905884f0-7546-4273-9061-12a790830beb/rwd_github_private/NESScovid19/data_temp/level0to3.fst', as.data.table=T) #still takes an annoying long time

}

library(dtplyr) #install.packages("dtplyr")
#names_to_gid_dt <- readRDS('/media/skynet2/905884f0-7546-4273-9061-12a790830beb/rwd_github_private/NESScovid19/data_temp/names_to_gid_dt.Rds') #do I want to bring in fst for this? or parquet?

library(fst)
#write_fst(names_to_gid_dt,'/media/skynet2/905884f0-7546-4273-9061-12a790830beb/rwd_github_private/NESScovid19/data_temp/names_to_gid_dt.fst', compress = 100) #upping the compression hoping it speeds up the read
level0to3 <- read_fst('/media/skynet2/905884f0-7546-4273-9061-12a790830beb/rwd_github_private/NESScovid19/data_temp/level0to3.fst', as.data.table=T) #still takes an annoying long time
class(level0to3)
dim(level0to3) #52,281,025 
head(level0to3)



```

Pull wikidata codes

```{r}

restartspark()

#Produce optimized versions of the file that are sorted, seperated, and more efficiently packed into fewer files

wikidata_labels_eng <- spark_read_parquet(sc=sc, name="wikidata_labels_eng", path='/media/skynet2/905884f0-7546-4273-9061-12a790830beb/rwd_github_private/NESSwikidata/data_out/wikidata_parq_optimized/level0=labels/level1=en', memory = F) 
replyr_nrow(wikidata_labels_eng) #48,936,919
head(wikidata_labels_eng) #

wikidata_aliases_eng <- spark_read_parquet(sc=sc, name="wikidata_alias_eng", path='/media/skynet2/905884f0-7546-4273-9061-12a790830beb/rwd_github_private/NESSwikidata/data_out/wikidata_parq_optimized/level0=aliases/level1=en', memory = F) 
replyr_nrow(wikidata_aliases_eng) #13,632,710
head(wikidata_aliases_eng) #

wikidata_aliaseslabels_eng <- rbind( #sparklyr actually prefers rbind
  wikidata_labels_eng %>% dplyr::select(wikidata_id,value),
  wikidata_aliases_eng %>% filter(level3=="value") %>% dplyr::select(wikidata_id,value)
)
replyr_nrow(wikidata_aliaseslabels_eng) #55,753,274

#If you are seeing this error in code that used to work, the most likely cause is a change dbplyr 1.4.0. Previously `df$x` or `df[[y]]` implied that `df` was a local variable, but now you must make that explict with `!!` or `local()`, e.g., `!!df$x`
#or `local(df[["y"]))
geonames_admin0_qcodes <- wikidata_aliaseslabels_eng %>% mutate(value=tolower(value)) %>% mutate(value=regexp_replace(value," ","")) %>% filter(value %in% !!geonames_admin0$name ) 

claims_P31 <- spark_read_parquet(sc=sc, name="claims", path="/media/skynet2/905884f0-7546-4273-9061-12a790830beb/rwd_github_private/NESSwikidata/data_out/wikidata_parq_optimized/level0=claims/level1=P31",memory = F) %>% 
              filter(level6=="id")  %>% filter(level3=="mainsnak") %>% dplyr::select(wikidata_id, P31=value)


#located in the administrative territorial entity (P131)
#country (Q6256)
#sovereign state (Q3624078)
#state with limited recognition (Q15634554)
#island nation (Q112099)
#British Overseas Territories (Q46395)
wikidata0 <- claims_P31 %>% filter(P31 %in% c('Q6256','Q3624078','Q15634554','Q112099','Q46395' )) %>% left_join(wikidata_aliases_eng) %>% filter(level3=="value") %>% dplyr::select(wikidata_id, value) %>% collect() %>% as.data.table()
dim(wikidata0)
temp <- wikidata0 %>% distinct() %>% count(value)

#hand drop dupes
#"Q58296","Q70802","Q161885","Q174193",
#As a good rule of thumb just pick the lowest nubmered one
library(stringi)
wikidata0_dt <- wikidata0 %>% distinct() %>% 
                         mutate(wikidata_id_numeric= str_replace(wikidata_id,"Q","") %>% as.numeric()) %>% 
                         mutate(name= value %>% rex_clean() ) %>% 
  
                         group_by(name) %>% filter(wikidata_id_numeric==min(wikidata_id_numeric)) %>% ungroup() %>%
                         dplyr::select(wikidata_id,name) %>% distinct()
dim(wikidata0_dt)

#this turned out to not work very well, the 279 hiearchy is too rough
#wikidata1
#We need everything that's a first-level administrative country subdivision
#first-level administrative country subdivision (Q10864048)
#claims_P279 <- spark_read_parquet(sc=sc, name="claims", path="/media/skynet2/905884f0-7546-4273-9061-12a790830beb/rwd_github_private/NESSwikidata/data_out/wikidata_parq_optimized/level0=claims/level1=P279",memory = F) %>% 
#               filter(level6=="id")  %>% filter(level3=="mainsnak") %>% dplyr::select(wikidata_id, P279=value)
#claims_P279_Q10864048 <- claims_P279 %>% filter(P279 == 'Q10864048')
#wikidata1 <- claims_P31 %>% inner_join(claims_P279_Q10864048 %>% dplyr::select(P31=wikidata_id)) %>% left_join(wikidata_aliases_eng) %>% filter(level3=="value") %>% dplyr::select(wikidata_id, value) %>% collect() %>% as.data.table()
#wikidata1_dt <- wikidata1 %>% distinct() %>% 
#                 mutate(wikidata_id_numeric= str_replace(wikidata_id,"Q","") %>% as.numeric()) %>% 
#                 mutate(name= value %>% rex_clean() ) %>% 
#  
#                 group_by(name) %>% filter(wikidata_id_numeric==min(wikidata_id_numeric)) %>% ungroup() %>%
#                 dplyr::select(wikidata_id,name) %>% distinct()
#dim(wikidata1_dt)

#This pulls every entity with a geonames id and all the labels and aliases for them
#GeoNames ID (P1566)
claims_P1566 <- spark_read_parquet(sc=sc, name="claims", path="/media/skynet2/905884f0-7546-4273-9061-12a790830beb/rwd_github_private/NESSwikidata/data_out/wikidata_parq_optimized/level0=claims/level1=P1566/level3=mainsnak",memory = F) #%>% 
              #filter(level6=="value") %>% dplyr::select(wikidata_id, P1566=value)
replyr_nrow(claims_P1566) #3683698

temp <- claims_P1566 %>% head(10000) %>% collect()

wikidata_togeonames <- claims_P1566 %>% dplyr::select(wikidata_id, geonames= value) %>% left_join(wikidata_aliaseslabels_eng) %>% collect() %>% as.data.table()
dim(wikidata_togeonames) #3,998,220
wikidata_togeonames_dt <- wikidata_togeonames  %>% distinct() %>% 
                           mutate(wikidata_id_numeric= str_replace(wikidata_id,"Q","") %>% as.numeric()) %>% 
                           mutate(name= value %>% rex_clean() ) %>% 
                           group_by(name) %>% filter(wikidata_id_numeric==min(wikidata_id_numeric)) %>% ungroup() %>%
                           dplyr::select(wikidata_id,geonames,name) %>% distinct()
dim(wikidata_togeonames_dt) #2,258,725 #227,663

#ISO 3166-1 alpha-2 code (P297) #nope we actually want the 2 digit code. god damn it.
#ISO 3166-1 alpha-3 code (P298) #we actually want the alpha code
#ISO 3166-1 numeric code (P299) #not the nmeric one here
claims_P297 <- spark_read_parquet(sc=sc, name="claims", path="/media/skynet2/905884f0-7546-4273-9061-12a790830beb/rwd_github_private/NESSwikidata/data_out/wikidata_parq_optimized/level0=claims/level1=P297/level3=mainsnak",memory = F) #%>% 
              #filter(level6=="value") %>% dplyr::select(wikidata_id, P1566=value)
replyr_nrow(claims_P297) #

wikidata_to_ISO31661 <- claims_P297 %>% dplyr::select(wikidata_id, ISO31661 = value) %>% left_join(wikidata_aliaseslabels_eng) %>% collect() %>% as.data.table()
wikidata_to_ISO31661_dt <- wikidata_to_ISO31661  %>% distinct() %>% 
                           mutate(wikidata_id_numeric= str_replace(wikidata_id,"Q","") %>% as.numeric()) %>% 
                           mutate(name= value %>% rex_clean() ) %>% 
                           group_by(name) %>% filter(wikidata_id_numeric==min(wikidata_id_numeric)) %>% ungroup() %>%
                           dplyr::select(wikidata_id,ISO31661,name) %>% distinct()
dim(wikidata_to_ISO31661_dt) #1455

#ISO 3166-2 code (P300)
claims_P300 <- spark_read_parquet(sc=sc, name="claims", path="/media/skynet2/905884f0-7546-4273-9061-12a790830beb/rwd_github_private/NESSwikidata/data_out/wikidata_parq_optimized/level0=claims/level1=P300/level3=mainsnak",memory = F) #%>% 
              #filter(level6=="value") %>% dplyr::select(wikidata_id, P1566=value)
replyr_nrow(claims_P300) #5474

#wikidata_aliases_eng %>% filter(wikidata_id=="Q13750") #for some reason label is missing
#wikidata_labels_eng %>% filter(wikidata_id=="Q13750") #nope I'm an idiot, I've only been joining on aliases alone



wikidata_to_ISO31662 <- claims_P300 %>% dplyr::select(wikidata_id, ISO31662 = value) %>% left_join(wikidata_aliaseslabels_eng) %>% collect() %>% as.data.table() #some of these labels are missing
wikidata_to_ISO31662_dt <- wikidata_to_ISO31662  %>% distinct() %>% 
                           mutate(wikidata_id_numeric= str_replace(wikidata_id,"Q","") %>% as.numeric()) %>% 
                           mutate(name= value %>% rex_clean() ) %>% 
                           group_by(name) %>% filter(wikidata_id_numeric==min(wikidata_id_numeric)) %>% ungroup() %>%
                           dplyr::select(wikidata_id,ISO31662,name) %>% distinct() %>%
                           mutate(ISO31661=substr(ISO31662,1,2))
dim(wikidata_to_ISO31662_dt) #8989

#

```



Geonames

```{r}


library(data.table)
geonames <- fread("/media/skynet2/905884f0-7546-4273-9061-12a790830beb/rwd_github_private/NESScovid19/data_temp/allCountries.txt", sep="\t")
dim(geonames) #12,006,426

#geonameid         : integer id of record in geonames database
#name              : name of geographical point (utf8) varchar(200)
#asciiname         : name of geographical point in plain ascii characters, varchar(200)
#alternatenames    : alternatenames, comma separated, ascii names automatically transliterated, convenience attribute from alternatename table, varchar(10000)
#latitude          : latitude in decimal degrees (wgs84)
#longitude         : longitude in decimal degrees (wgs84)
#feature class     : see http://www.geonames.org/export/codes.html, char(1)
#feature code      : see http://www.geonames.org/export/codes.html, varchar(10)
#country code      : ISO-3166 2-letter country code, 2 characters
#cc2               : alternate country codes, comma separated, ISO-3166 2-letter country code, 200 characters
#admin1 code       : fipscode (subject to change to iso code), see exceptions below, see file admin1Codes.txt for display names of this code; varchar(20)
#admin2 code       : code for the second administrative division, a county in the US, see file admin2Codes.txt; varchar(80) 
#admin3 code       : code for third level administrative division, varchar(20)
#admin4 code       : code for fourth level administrative division, varchar(20)
#population        : bigint (8 byte int) 
#elevation         : in meters, integer
#dem               : digital elevation model, srtm3 or gtopo30, average elevation of 3''x3'' (ca 90mx90m) or 30''x30'' (ca 900mx900m) area in meters, integer. srtm processed by cgiar/ciat.
#timezone          : the iana timezone id (see file timeZone.txt) varchar(40)
#modification date : date of last modification in yyyy-MM-dd format

vars <- c('geonameid','name','asciiname','alternatenames','latitude','longitude','feature_class','feature_code','country_code','cc2','admin1','admin2','admin3','admin4','population','elevation','dem','timezone','modification')
names(geonames) <- vars

test <- geonames %>% filter(name %in% "San Antonio") 

table(geonames$feature_class) %>% sort()
table(geonames$feature_code) %>% sort()

geonames %>% filter(feature_code %in% 'ADMD')

geonames_p <- geonames  %>% filter(!is.na(admin2) & admin2!='' ) #%>% filter(feature_class=="P") #& feature_class=="P"
dim(geonames_p) #4,770,851

geonames_p_unique <- geonames_p %>% group_by(country_code, name) %>% arrange(-population) %>% filter(row_number()==1) %>% ungroup() #for every placename, keep only the most populated with that name per country. Use this to put in Cities

#hierachy is missing some, like san antonio for some reason 4726206
#let's add them back in
hierarchy <- fread("/media/skynet2/905884f0-7546-4273-9061-12a790830beb/rwd_github_private/NESScovid19/data_temp/hierarchy.txt", sep="\t")

#add these nestings
#unitedkingdom	 england
#unitedkingdom	 northernireland
#unitedkingdom	 scotland
#unitedkingdom	 wales
hierarchy <- rbindlist(list(hierarchy,
data.table(V1=2635167, V2=6269131),
data.table(V1=2635167, V2=2641364),
data.table(V1=2635167,V2=2638360),
data.table(V1=2635167,V2=2634895)
), fill=T)

dim(hierarchy) #488,103
library(igraph)
library(tictoc)
#vec <- 1:100000 #100k to 66 seconds whole thing is only 488k so this is fine. Nope apparently it's much longer than that for the full graph. Lots of branching nodes.
#1552.91 sec elapsed #took about 25 minutes
vec <- 1:nrow(hierarchy) #1:100000#
g <- graph.data.frame(hierarchy[vec,c(2,1)], #from and to so invert the columns
                 directed=TRUE, vertices=NULL)
#The root should be 6295630
#reachable
earth = V(g)[name=="6295630"]
#g_all <- subcomponent(g,
#             v=earth,
#             mode = c("in"))

#Could have also just done a bunch of joins. Probably would have been better.
path <- "/media/skynet2/905884f0-7546-4273-9061-12a790830beb/rwd_github_private/NESScovid19/data_temp/geonames_hierarchy_paths.txt"
fromscratch=F
if(fromscratch){
  tic()
  #shortest <- get.shortest.paths(graph=g,
  #                               from=earth,
  #                               mode = "in") #this is going to be really big
  all_shortest_paths <- get.shortest.paths(graph=g, #switching to all shortest paths to allow for multiple routes, e.g. england as a country or a admin1 under the UK
                                 from=earth,
                                 mode = "in") #this is going to be really big
  toc()
  saveRDS(shortest,"/media/skynet2/905884f0-7546-4273-9061-12a790830beb/rwd_github_private/NESScovid19/data_temp/geonames_shortest_path.rds")

  shortest <- readRDS("/media/skynet2/905884f0-7546-4273-9061-12a790830beb/rwd_github_private/NESScovid19/data_temp/geonames_shortest_path.rds")
  class(shortest)
  length(shortest) #516,803
  length(shortest[[1]])
  shortest[[1]][[1]]
  
  #we can iterate over this and just write them to a file and read back
  #This is slow, I don't care I just need this done right now
  tic()
  list_of_df <- lapply(vec, FUN=function(i)  data.frame( t(names(shortest[[1]][[i]]) ))) #it still takes a while
  list_of_dt <- rbindlist(list_of_df, fill=T)
  toc()

}
#readLines(path, n=1)
#geonames_hierarchy_paths <- unique( read.table(file=path, sep="\t", fill=T, header = FALSE, col.names=paste("V", 1:20, sep="")) )
#dim(geonames_hierarchy_paths) # 308797     20
#geonames_hierarchy_paths <- as.data.table(geonames_hierarchy_paths[,colSums(is.na(geonames_hierarchy_paths))!=nrow(geonames_hierarchy_paths)])

geonames_inpaths <- unique(c(hierarchy$V1,hierarchy$V2)) # length(geonames_inpaths) #516,803


#The table 'alternate names' :
#-----------------------------
#alternateNameId   : the id of this alternate name, int
#geonameid         : geonameId referring to id in table 'geoname', int
#isolanguage       : iso 639 language code 2- or 3-characters; 4-characters 'post' for postal codes and 'iata','icao' and faac for airport codes, fr_1793 for French Revolution names,  abbr for abbreviation, link to a website (mostly to #wikipedia), wkdt for the wikidataid, varchar(7)
#alternate name    : alternate name or name variant, varchar(400)
#isPreferredName   : '1', if this alternate name is an official/preferred name
#isShortName       : '1', if this is a short name like 'California' for 'State of California'
#isColloquial      : '1', if this alternate name is a colloquial or slang term. Example: 'Big Apple' for 'New York'.
#isHistoric        : '1', if this alternate name is historic and was used in the past. Example 'Bombay' for 'Mumbai'.
#from		  : from period when the name was used
#to		  : to period when the name was used
alternateNamesV2 <- fread("/media/skynet2/905884f0-7546-4273-9061-12a790830beb/rwd_github_private/NESScovid19/data_temp/alternateNamesV2/alternateNamesV2.txt", sep="\t")
dim(alternateNamesV2) #14,984,570
table(alternateNamesV2$V3)
alternateNamesV2_eng <- alternateNamesV2 %>% dplyr::select(geonameid=V2,name=V4, lang=V3)  %>% dplyr::filter(lang %in% c('','en')) %>% dplyr::filter(geonameid %in% geonames_inpaths) #,'link'
dim(alternateNamesV2_eng) #479,596
alternateNamesV2_enwiki <- alternateNamesV2 %>% 
                            dplyr::select(geonameid=V2,enwiki=V4, lang=V3)  %>% 
                            dplyr::filter(lang %in% c('link')) %>% dplyr::filter(geonameid %in% geonames_inpaths) %>% 
                            filter(str_detect(enwiki, "https://en.wikipedia.org"))

#now rexclean
library(stringi)
rex_clean <- function(x){ x %>% stri_trans_general("latin-ascii") %>% stri_replace_all(regex="[^A-Za-z0-9]","") %>% tolower() } #so individually, each string should be devoid of spaces,noncharacters, and nonlatin

tic()
geonames_idtoname <- bind_rows(
  geonames %>% dplyr::select(geonameid,name) %>% filter(geonameid %in% geonames_inpaths),
  geonames %>% dplyr::select(geonameid,name=asciiname) %>% filter(geonameid %in% geonames_inpaths),
  #We can start small with just the regular names and then go back and add these
  alternateNamesV2_eng %>% dplyr::select(geonameid,name) %>% filter(geonameid %in% geonames_inpaths) 
) %>% 
    mutate(name  = rex_clean(name)) %>% #this is what's expensive 
    mutate(name = trimws(name)) %>%
    filter(!is.na(name) & name!='') %>%
    distinct() %>%
  left_join(geonames %>% dplyr::select(geonameid,feature_code) ) %>% 
  filter(!feature_code %in% c('HTL','BLDG','AIRP','SEA','HSE'))


dim(geonames_idtoname) #605,632    

#Let's do admin0 first
#this adds wikidata codes to geonames codes
geonames_admin0 <- geonames_hierarchy_paths %>% dplyr::select(geonameid=V3) %>% distinct() %>% na.omit() %>% left_join(geonames_idtoname) %>% left_join(alternateNamesV2_enwiki %>% dplyr::select(-lang)) %>% distinct() %>% 
                   mutate(geonameid=as.character(geonameid)) %>%
                   left_join(wikidata_togeonames_dt %>% dplyr::select(geonameid=geonames, wikidata_id) ) %>% distinct() 
#this grabs extra labels and aliases
geonames_admin0 <- bind_rows(
  geonames_admin0,
  wikidata_togeonames_dt %>% dplyr::select(geonameid=geonames, wikidata_id, name) %>% inner_join(geonames_admin0 %>% dplyr::select(geonameid) %>% distinct())
) %>% distinct() %>% #I don't know why we ended up with dupes again but again pick the one with the lowest q code
  mutate(wikidata_id_numeric= str_replace(wikidata_id,"Q","") %>% as.numeric()) %>% 
   group_by(name) %>% filter(wikidata_id_numeric==min(wikidata_id_numeric)) %>% ungroup() %>% 
   arrange(geonameid,feature_code) %>% group_by(geonameid ) %>% fill(feature_code) %>% ungroup() %>% #fill down feature code
   dplyr::select(-wikidata_id_numeric) %>% distinct()

test <- geonames_admin0 %>% count(name) #ok no dupes now. every name is matched once and only once

geonames_admin1 <- geonames_hierarchy_paths %>% dplyr::select(geonameid0=V3, geonameid1=V4) %>% distinct() %>% na.omit() %>%
                   left_join(geonames_idtoname %>% dplyr::select(geonameid1=geonameid,name1=name, feature_code1=feature_code)) %>% distinct() %>%  arrange(geonameid0,geonameid1, name1) %>% mutate_if(is.numeric, as.character) %>%
                   left_join(geonames_admin0 %>% dplyr::select(geonameid0=geonameid,wikidata_id0=wikidata_id)) %>%
                   left_join(wikidata_togeonames_dt %>% dplyr::select(geonameid1=geonames, wikidata_id1=wikidata_id) ) %>% distinct() 
geonames_admin1 <- bind_rows(
  geonames_admin1,
  wikidata_togeonames_dt %>% dplyr::select(geonameid1=geonames, wikidata_id1=wikidata_id, name1=name) %>% inner_join(geonames_admin1 %>% dplyr::select(geonameid1) %>% distinct())
) %>% distinct() %>% 
  
  #I don't know why we ended up with dupes again but again pick the one with the lowest q code

  mutate(wikidata_id0_numeric= str_replace(wikidata_id0,"Q","") %>% as.numeric())  %>% 
  group_by(geonameid0,name1) %>% filter(wikidata_id0_numeric==min(wikidata_id0_numeric)) %>% ungroup() %>% 
  dplyr::select(-wikidata_id0_numeric) %>% distinct()  %>%

  mutate(wikidata_id1_numeric= str_replace(wikidata_id1,"Q","") %>% as.numeric())  %>% 
  group_by(geonameid0,name1) %>% filter(wikidata_id1_numeric==min(wikidata_id1_numeric)) %>% ungroup() %>% 
  dplyr::select(-wikidata_id1_numeric) %>% distinct()

test <- geonames_admin1 %>% count(geonameid0,name1) #ok no dupes now. every name is matched once and only once


geonames_admin2 <- geonames_hierarchy_paths %>% dplyr::select(geonameid0=V3, geonameid1=V4, geonameid2=V5) %>% distinct() %>% na.omit() %>%
                    left_join(geonames_idtoname %>% dplyr::select(geonameid2=geonameid,name2=name, feature_code2=feature_code)) %>% distinct() %>%  arrange(geonameid0,geonameid1,geonameid2, name2)

```




Combine countries, geonames, and admin into one admin0

```{r}

#devtools::install_github("moodymudskipper/safejoin")
library(safejoin)

temp2 <- alternateNamesV2_enwiki %>% count(geonameid)

#gadm36_df = st_read("/media/skynet2/905884f0-7546-4273-9061-12a790830beb/rwd_github_private/NESSgadm/data_in/gadm36_gpkg/gadm36.gpkg") %>% as.data.frame()
#gadm36_admin0 <- gadm36_df %>% dplyr::select(gadm36=GID_0, name=NAME_0 ) %>% distinct() %>% mutate(name  = rex_clean(name))
#  
geonames_admin0 <- geonames_hierarchy_paths %>% dplyr::select(geonameid=V3) %>% distinct() %>% na.omit() %>% left_join(geonames_idtoname) %>% 
                   arrange(geonameid, name)  %>% distinct() %>% na.omit()  

admin0 <- geonames_admin0 %>% distinct() %>%
          safe_full_join(wikidata0_dt %>% distinct(), conflict=NULL ) %>% distinct() %>%  #This pads it out to any that didn't get wikidata codes the first time 
          safe_full_join(countries_df_unique , conflict=NULL ) %>% distinct() %>% 
          safe_full_join(wikidata_to_ISO31661_dt %>% dplyr::select(wikidata_id,ISO31661), conflict=coalesce  ) %>% distinct() %>%
          safe_full_join(wikidata_to_ISO31661_dt %>% dplyr::select(wikidata_id,name), conflict=coalesce  ) %>% distinct() %>% #This pads it out to any that didn't get wikidata codes the first time 
          mutate_if(is.numeric,as.character) %>% mutate_if(is.factor,as.character) %>%
  
          safe_full_join(wikidata_togeonames_dt %>% dplyr::select(geonameid=geonames, wikidata_id=wikidata_id), by="wikidata_id", conflict = coalesce ) %>% distinct() %>% filter(!is.na(name)) %>% 
          mutate_if(is.numeric,as.character) %>% mutate_if(is.factor,as.character) %>%
  
          safe_full_join(wikidata_togeonames_dt %>% dplyr::select(geonameid=geonames, wikidata_id=wikidata_id), by="geonameid", conflict = coalesce ) %>% distinct() %>% filter(!is.na(name)) %>%
          mutate_if(is.numeric,as.character) %>% mutate_if(is.factor,as.character) %>%
  
          #gid
          arrange(gid,geonameid)    %>% group_by(gid) %>% mutate(temp=geonameid) %>% fill(temp) %>% mutate(geonameid=ifelse(!is.na(gid), temp, geonameid)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid,wikidata_id)    %>% group_by(gid) %>% mutate(temp=wikidata_id) %>% fill(temp) %>% mutate(wikidata_id=ifelse(!is.na(gid), temp, wikidata_id)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid,ISO31661)    %>% group_by(gid) %>% mutate(temp=ISO31661) %>% fill(temp) %>% mutate(ISO31661=ifelse(!is.na(gid), temp, ISO31661)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid,feature_code)    %>% group_by(gid) %>% mutate(temp=feature_code) %>% fill(temp) %>% mutate(feature_code=ifelse(!is.na(gid), temp, feature_code)) %>% dplyr::select(-temp) %>% ungroup() %>%

          #geoname
          arrange(geonameid,gid)    %>% group_by(geonameid) %>% mutate(temp=gid) %>% fill(temp) %>% mutate(gid=ifelse(!is.na(geonameid), temp, gid)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(geonameid,wikidata_id)    %>% group_by(geonameid) %>% mutate(temp=wikidata_id) %>% fill(temp) %>% mutate(wikidata_id=ifelse(!is.na(geonameid), temp, wikidata_id)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(geonameid,ISO31661)    %>% group_by(geonameid) %>% mutate(temp=ISO31661) %>% fill(temp) %>% mutate(ISO31661=ifelse(!is.na(geonameid), temp, ISO31661)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(geonameid,feature_code)    %>% group_by(geonameid) %>% mutate(temp=feature_code) %>% fill(temp) %>% mutate(feature_code=ifelse(!is.na(geonameid), temp, feature_code)) %>% dplyr::select(-temp) %>% ungroup() %>%

          #wikidata_id
          arrange(wikidata_id,gid)         %>% group_by(wikidata_id) %>% mutate(temp=gid)         %>% fill(temp) %>% mutate(gid=ifelse(!is.na(wikidata_id), temp, gid)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(wikidata_id,ISO31661)    %>% group_by(wikidata_id) %>% mutate(temp=ISO31661)    %>% fill(temp) %>% mutate(ISO31661=ifelse(!is.na(wikidata_id), temp, ISO31661)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(wikidata_id,feature_code)%>% group_by(wikidata_id) %>% mutate(temp=feature_code)%>% fill(temp) %>% mutate(feature_code=ifelse(!is.na(wikidata_id), temp, feature_code)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(wikidata_id,geonameid)   %>% group_by(wikidata_id) %>% mutate(temp=geonameid)   %>% fill(temp) %>% mutate(geonameid=ifelse(!is.na(wikidata_id), temp, geonameid)) %>% dplyr::select(-temp) %>% ungroup() %>%

          mutate_if(is.numeric,as.character) %>% mutate_if(is.factor,as.character) %>%
          rename(admin0_name_clean=name , geonameid0=geonameid , feature_code0=feature_code,wikidata_id0=wikidata_id,  gid0=gid)
dim(admin0) #15,917

admin0 <- admin0 %>% filter(!geonameid0 %in% c(7729900))

#wikidata on admin1 is a mess so we're joining on geonames code instead
admin1 <- admin0 %>% dplyr::select(-admin0_name_clean,-feature_code0) %>% distinct() %>% 
          mutate_if(is.numeric,as.character) %>% mutate_if(is.factor,as.character) %>%
  
          safe_full_join(geonames_admin1 %>% distinct() %>% filter(!is.na(name1))  , conflict = coalesce, by="geonameid0"  )  %>% distinct() %>% 
          mutate_if(is.numeric,as.character) %>% mutate_if(is.factor,as.character) %>%
  
          safe_full_join(gadm1 %>% distinct()  %>% filter(!is.na(name1)) , conflict = coalesce ) %>% distinct() %>%
          mutate_if(is.numeric,as.character) %>% mutate_if(is.factor,as.character) %>%
  
          safe_full_join(wikidata_to_ISO31662_dt %>% dplyr::select(wikidata_id1=wikidata_id, ISO31662, name1=name, ISO31661)  %>% distinct() %>% filter(!is.na(name1)) , conflict = coalesce  ) %>% distinct() %>%
          mutate_if(is.numeric,as.character) %>% mutate_if(is.factor,as.character) %>%
  
          #we can get back some geonames ids from their q codes that aren't in the geonames hierarchy correctly
          safe_full_join(wikidata_togeonames_dt %>% dplyr::select(geonameid1=geonames, wikidata_id1=wikidata_id), by="wikidata_id1", conflict = coalesce ) %>% distinct() %>% filter(!is.na(name1)) %>% 
          safe_full_join(wikidata_togeonames_dt %>% dplyr::select(geonameid1=geonames, wikidata_id1=wikidata_id), by="geonameid1", conflict = coalesce ) %>% distinct() %>% filter(!is.na(name1)) %>%
          mutate_if(is.numeric,as.character) %>% mutate_if(is.factor,as.character) %>%
  
          #Gid  
          arrange(gid1,gid0)                %>% group_by(gid1) %>% mutate(temp=gid0) %>% fill(temp) %>% mutate(gid0=ifelse(!is.na(gid1), temp, gid0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid1,geonameid0)                %>% group_by(gid1) %>% mutate(temp=geonameid0) %>% fill(temp) %>% mutate(geonameid0=ifelse(!is.na(gid1), temp, geonameid0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid1,geonameid1)                %>% group_by(gid1) %>% mutate(temp=geonameid1) %>% fill(temp) %>% mutate(geonameid1=ifelse(!is.na(gid1), temp, geonameid1)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid1,feature_code1)                %>% group_by(gid1) %>% mutate(temp=feature_code1) %>% fill(temp) %>% mutate(feature_code1=ifelse(!is.na(gid1), temp, feature_code1)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid1,wikidata_id0)                %>% group_by(gid1) %>% mutate(temp=wikidata_id0) %>% fill(temp) %>% mutate(wikidata_id0=ifelse(!is.na(gid1), temp, wikidata_id0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid1,wikidata_id1)                %>% group_by(gid1) %>% mutate(temp=wikidata_id1) %>% fill(temp) %>% mutate(wikidata_id1=ifelse(!is.na(gid1), temp, wikidata_id1)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid1,ISO31661)                %>% group_by(gid1) %>% mutate(temp=ISO31661) %>% fill(temp) %>% mutate(ISO31661=ifelse(!is.na(gid1), temp, ISO31661)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid1,ISO31662)                %>% group_by(gid1) %>% mutate(temp=ISO31662) %>% fill(temp) %>% mutate(ISO31662=ifelse(!is.na(gid1), temp, ISO31662)) %>% dplyr::select(-temp) %>% ungroup() %>%

          #ISO31662
          arrange(ISO31662,geonameid0)                %>% group_by(ISO31662) %>% mutate(temp=geonameid0) %>% fill(temp) %>% mutate(geonameid0=ifelse(!is.na(ISO31662), temp, geonameid0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(ISO31662,geonameid1)                %>% group_by(ISO31662) %>% mutate(temp=geonameid1) %>% fill(temp) %>% mutate(geonameid1=ifelse(!is.na(ISO31662), temp, geonameid1)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(ISO31662,wikidata_id0)                %>% group_by(ISO31662) %>% mutate(temp=wikidata_id0) %>% fill(temp) %>% mutate(wikidata_id0=ifelse(!is.na(ISO31662), temp, wikidata_id0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(ISO31662,wikidata_id1)                %>% group_by(ISO31662) %>% mutate(temp=wikidata_id1) %>% fill(temp) %>% mutate(wikidata_id1=ifelse(!is.na(ISO31662), temp, wikidata_id1)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(ISO31662,gid0)                %>% group_by(ISO31662) %>% mutate(temp=gid0) %>% fill(temp) %>% mutate(gid0=ifelse(!is.na(ISO31662), temp, gid0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(ISO31662,gid1)                %>% group_by(ISO31662) %>% mutate(temp=gid1) %>% fill(temp) %>% mutate(gid1=ifelse(!is.na(ISO31662), temp, gid1)) %>% dplyr::select(-temp) %>% ungroup() %>%
  
          #wikidata_id1
          arrange(wikidata_id1,geonameid0)                %>% group_by(wikidata_id1) %>% mutate(temp=geonameid0) %>% fill(temp) %>% mutate(geonameid0=ifelse(!is.na(wikidata_id1), temp, geonameid0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(wikidata_id1,geonameid1)                %>% group_by(wikidata_id1) %>% mutate(temp=geonameid1) %>% fill(temp) %>% mutate(geonameid1=ifelse(!is.na(wikidata_id1), temp, geonameid1)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(wikidata_id1,ISO31661)                %>% group_by(wikidata_id1) %>% mutate(temp=ISO31661) %>% fill(temp) %>% mutate(ISO31661=ifelse(!is.na(wikidata_id1), temp, ISO31661)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(wikidata_id1,ISO31662)                %>% group_by(wikidata_id1) %>% mutate(temp=ISO31662) %>% fill(temp) %>% mutate(ISO31662=ifelse(!is.na(wikidata_id1), temp, ISO31662)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(wikidata_id1,gid0)                %>% group_by(wikidata_id1) %>% mutate(temp=gid0) %>% fill(temp) %>% mutate(gid0=ifelse(!is.na(wikidata_id1), temp, gid0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(wikidata_id1,gid1)                %>% group_by(wikidata_id1) %>% mutate(temp=gid1) %>% fill(temp) %>% mutate(gid1=ifelse(!is.na(wikidata_id1), temp, gid1)) %>% dplyr::select(-temp) %>% ungroup() %>%
  
          #ISO31661
          arrange(ISO31661,geonameid0)                %>% group_by(ISO31661) %>% mutate(temp=geonameid0) %>% fill(temp) %>% mutate(geonameid0=ifelse(!is.na(ISO31661), temp, geonameid0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(ISO31661,gid0)                %>% group_by(ISO31661) %>% mutate(temp=gid0) %>% fill(temp) %>% mutate(gid0=ifelse(!is.na(ISO31661), temp, gid0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(ISO31661,wikidata_id0)                %>% group_by(ISO31661) %>% mutate(temp=wikidata_id0) %>% fill(temp) %>% mutate(wikidata_id0=ifelse(!is.na(ISO31661), temp, wikidata_id0)) %>% dplyr::select(-temp) %>% ungroup() %>%

          #geonames
          #it's using NA as a grouping variable which is not what we want
          arrange(geonameid1,gid0)                %>% group_by(geonameid1) %>% mutate(temp=gid0) %>% fill(temp) %>% mutate(gid0=ifelse(!is.na(geonameid1), temp, gid0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(geonameid1,gid1)                %>% group_by(geonameid1) %>% mutate(temp=gid1) %>% fill(temp) %>% mutate(gid1=ifelse(!is.na(geonameid1), temp, gid1)) %>% dplyr::select(-temp) %>% ungroup() %>%
  
          arrange(geonameid1,wikidata_id0)        %>% group_by(geonameid1) %>% mutate(temp=wikidata_id0) %>% fill(temp) %>% mutate(wikidata_id0=ifelse(!is.na(geonameid1), temp, wikidata_id0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(geonameid1,wikidata_id1)        %>% group_by(geonameid1) %>% mutate(temp=wikidata_id1) %>% fill(temp) %>% mutate(wikidata_id1=ifelse(!is.na(geonameid1), temp, wikidata_id1)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(geonameid1,ISO31661)            %>% group_by(geonameid1) %>% mutate(temp=ISO31661) %>% fill(temp) %>% mutate(ISO31661=ifelse(!is.na(geonameid1), temp, ISO31661)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(geonameid1,ISO31662)            %>% group_by(geonameid1) %>% mutate(temp=ISO31662) %>% fill(temp) %>% mutate(ISO31662=ifelse(!is.na(geonameid1), temp, ISO31662)) %>% dplyr::select(-temp) %>% ungroup() %>%

          #level0
          arrange(gid0,geonameid0)                %>% group_by(gid0) %>% mutate(temp=geonameid0) %>% fill(temp) %>% mutate(geonameid0=ifelse(!is.na(gid0), temp, geonameid0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid0,ISO31661)                %>% group_by(gid0) %>% mutate(temp=ISO31661) %>% fill(temp) %>% mutate(ISO31661=ifelse(!is.na(ISO31661), temp, ISO31661)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid0,wikidata_id0)                %>% group_by(gid0) %>% mutate(temp=wikidata_id0) %>% fill(temp) %>% mutate(wikidata_id0=ifelse(!is.na(gid0), temp, wikidata_id0)) %>% dplyr::select(-temp) %>% ungroup() %>%
  
          #some of these names are dupes and we can group by that now and go down
          filter(!is.na(name1)) %>% #make sure again that all the names are the
          arrange(gid0,name1,geonameid0)        %>% group_by(gid0,name1) %>% mutate(temp=geonameid0) %>% fill(temp) %>% mutate(geonameid0=ifelse(!is.na(gid0), temp, geonameid0)) %>% dplyr::select(-temp) %>% ungroup() %>%
  
          arrange(gid0,name1,gid1)                %>% group_by(gid0,name1) %>% mutate(temp=gid1) %>% fill(temp) %>% mutate(gid1=ifelse(!is.na(gid1), temp, gid1)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid0,name1,geonameid0)                %>% group_by(gid0,name1) %>% mutate(temp=geonameid0) %>% fill(temp) %>% mutate(geonameid0=ifelse(!is.na(gid0), temp, geonameid0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid0,name1,geonameid1)                %>% group_by(gid0,name1) %>% mutate(temp=geonameid1) %>% fill(temp) %>% mutate(geonameid1=ifelse(!is.na(gid0), temp, geonameid1)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid0,name1,feature_code1)                %>% group_by(gid0,name1) %>% mutate(temp=feature_code1) %>% fill(temp) %>% mutate(feature_code1=ifelse(!is.na(gid0), temp, feature_code1)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid0,name1,wikidata_id0)                %>% group_by(gid0,name1) %>% mutate(temp=wikidata_id0) %>% fill(temp) %>% mutate(wikidata_id0=ifelse(!is.na(gid0), temp, wikidata_id0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid0,name1,wikidata_id1)                %>% group_by(gid0,name1) %>% mutate(temp=wikidata_id1) %>% fill(temp) %>% mutate(wikidata_id1=ifelse(!is.na(gid0), temp, wikidata_id1)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid0,name1,ISO31661)                %>% group_by(gid0,name1) %>% mutate(temp=ISO31661) %>% fill(temp) %>% mutate(ISO31661=ifelse(!is.na(gid0), temp, ISO31661)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid0,name1,ISO31662)                %>% group_by(gid0,name1) %>% mutate(temp=ISO31662) %>% fill(temp) %>% mutate(ISO31662=ifelse(!is.na(gid0), temp, ISO31662)) %>% dplyr::select(-temp) %>% ungroup() %>%

  
          #do geonames again
          #it's using NA as a grouping variable which is not what we want
          arrange(geonameid1,gid0)                %>% group_by(geonameid1) %>% mutate(temp=gid0) %>% fill(temp) %>% mutate(gid0=ifelse(!is.na(geonameid1), temp, gid0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(geonameid1,gid1)                %>% group_by(geonameid1) %>% mutate(temp=gid1) %>% fill(temp) %>% mutate(gid1=ifelse(!is.na(geonameid1), temp, gid1)) %>% dplyr::select(-temp) %>% ungroup() %>%
  
          arrange(geonameid1,wikidata_id0)        %>% group_by(geonameid1) %>% mutate(temp=wikidata_id0) %>% fill(temp) %>% mutate(wikidata_id0=ifelse(!is.na(geonameid1), temp, wikidata_id0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(geonameid1,wikidata_id1)        %>% group_by(geonameid1) %>% mutate(temp=wikidata_id1) %>% fill(temp) %>% mutate(wikidata_id1=ifelse(!is.na(geonameid1), temp, wikidata_id1)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(geonameid1,ISO31661)            %>% group_by(geonameid1) %>% mutate(temp=ISO31661) %>% fill(temp) %>% mutate(ISO31661=ifelse(!is.na(geonameid1), temp, ISO31661)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(geonameid1,ISO31662)            %>% group_by(geonameid1) %>% mutate(temp=ISO31662) %>% fill(temp) %>% mutate(ISO31662=ifelse(!is.na(geonameid1), temp, ISO31662)) %>% dplyr::select(-temp) %>% ungroup() %>%

  
            #Gid  
          arrange(gid1,gid0)                %>% group_by(gid1) %>% mutate(temp=gid0) %>% fill(temp) %>% mutate(gid0=ifelse(!is.na(gid1), temp, gid0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid1,geonameid0)                %>% group_by(gid1) %>% mutate(temp=geonameid0) %>% fill(temp) %>% mutate(geonameid0=ifelse(!is.na(gid1), temp, geonameid0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid1,geonameid1)                %>% group_by(gid1) %>% mutate(temp=geonameid1) %>% fill(temp) %>% mutate(geonameid1=ifelse(!is.na(gid1), temp, geonameid1)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid1,feature_code1)                %>% group_by(gid1) %>% mutate(temp=feature_code1) %>% fill(temp) %>% mutate(feature_code1=ifelse(!is.na(gid1), temp, feature_code1)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid1,wikidata_id0)                %>% group_by(gid1) %>% mutate(temp=wikidata_id0) %>% fill(temp) %>% mutate(wikidata_id0=ifelse(!is.na(gid1), temp, wikidata_id0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid1,wikidata_id1)                %>% group_by(gid1) %>% mutate(temp=wikidata_id1) %>% fill(temp) %>% mutate(wikidata_id1=ifelse(!is.na(gid1), temp, wikidata_id1)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid1,ISO31661)                %>% group_by(gid1) %>% mutate(temp=ISO31661) %>% fill(temp) %>% mutate(ISO31661=ifelse(!is.na(gid1), temp, ISO31661)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid1,ISO31662)                %>% group_by(gid1) %>% mutate(temp=ISO31662) %>% fill(temp) %>% mutate(ISO31662=ifelse(!is.na(gid1), temp, ISO31662)) %>% dplyr::select(-temp) %>% ungroup() %>%

          #ISO31662
          arrange(ISO31662,geonameid0)                %>% group_by(ISO31662) %>% mutate(temp=geonameid0) %>% fill(temp) %>% mutate(geonameid0=ifelse(!is.na(ISO31662), temp, geonameid0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(ISO31662,geonameid1)                %>% group_by(ISO31662) %>% mutate(temp=geonameid1) %>% fill(temp) %>% mutate(geonameid1=ifelse(!is.na(ISO31662), temp, geonameid1)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(ISO31662,wikidata_id0)                %>% group_by(ISO31662) %>% mutate(temp=wikidata_id0) %>% fill(temp) %>% mutate(wikidata_id0=ifelse(!is.na(ISO31662), temp, wikidata_id0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(ISO31662,wikidata_id1)                %>% group_by(ISO31662) %>% mutate(temp=wikidata_id1) %>% fill(temp) %>% mutate(wikidata_id1=ifelse(!is.na(ISO31662), temp, wikidata_id1)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(ISO31662,gid0)                %>% group_by(ISO31662) %>% mutate(temp=gid0) %>% fill(temp) %>% mutate(gid0=ifelse(!is.na(ISO31662), temp, gid0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(ISO31662,gid1)                %>% group_by(ISO31662) %>% mutate(temp=gid1) %>% fill(temp) %>% mutate(gid1=ifelse(!is.na(ISO31662), temp, gid1)) %>% dplyr::select(-temp) %>% ungroup() %>%
  
          #wikidata_id1
          arrange(wikidata_id1,geonameid0)                %>% group_by(wikidata_id1) %>% mutate(temp=geonameid0) %>% fill(temp) %>% mutate(geonameid0=ifelse(!is.na(wikidata_id1), temp, geonameid0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(wikidata_id1,geonameid1)                %>% group_by(wikidata_id1) %>% mutate(temp=geonameid1) %>% fill(temp) %>% mutate(geonameid1=ifelse(!is.na(wikidata_id1), temp, geonameid1)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(wikidata_id1,ISO31661)                %>% group_by(wikidata_id1) %>% mutate(temp=ISO31661) %>% fill(temp) %>% mutate(ISO31661=ifelse(!is.na(wikidata_id1), temp, ISO31661)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(wikidata_id1,ISO31662)                %>% group_by(wikidata_id1) %>% mutate(temp=ISO31662) %>% fill(temp) %>% mutate(ISO31662=ifelse(!is.na(wikidata_id1), temp, ISO31662)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(wikidata_id1,gid0)                %>% group_by(wikidata_id1) %>% mutate(temp=gid0) %>% fill(temp) %>% mutate(gid0=ifelse(!is.na(wikidata_id1), temp, gid0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(wikidata_id1,gid1)                %>% group_by(wikidata_id1) %>% mutate(temp=gid1) %>% fill(temp) %>% mutate(gid1=ifelse(!is.na(wikidata_id1), temp, gid1)) %>% dplyr::select(-temp) %>% ungroup() %>%
  
          #ISO31661
          arrange(ISO31661,geonameid0)                %>% group_by(ISO31661) %>% mutate(temp=geonameid0) %>% fill(temp) %>% mutate(geonameid0=ifelse(!is.na(ISO31661), temp, geonameid0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(ISO31661,gid0)                %>% group_by(ISO31661) %>% mutate(temp=gid0) %>% fill(temp) %>% mutate(gid0=ifelse(!is.na(ISO31661), temp, gid0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(ISO31661,wikidata_id0)                %>% group_by(ISO31661) %>% mutate(temp=wikidata_id0) %>% fill(temp) %>% mutate(wikidata_id0=ifelse(!is.na(ISO31661), temp, wikidata_id0)) %>% dplyr::select(-temp) %>% ungroup() %>%

          #geonames
          #it's using NA as a grouping variable which is not what we want
          arrange(geonameid1,gid0)                %>% group_by(geonameid1) %>% mutate(temp=gid0) %>% fill(temp) %>% mutate(gid0=ifelse(!is.na(geonameid1), temp, gid0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(geonameid1,gid1)                %>% group_by(geonameid1) %>% mutate(temp=gid1) %>% fill(temp) %>% mutate(gid1=ifelse(!is.na(geonameid1), temp, gid1)) %>% dplyr::select(-temp) %>% ungroup() %>%
  
          arrange(geonameid1,wikidata_id0)        %>% group_by(geonameid1) %>% mutate(temp=wikidata_id0) %>% fill(temp) %>% mutate(wikidata_id0=ifelse(!is.na(geonameid1), temp, wikidata_id0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(geonameid1,wikidata_id1)        %>% group_by(geonameid1) %>% mutate(temp=wikidata_id1) %>% fill(temp) %>% mutate(wikidata_id1=ifelse(!is.na(geonameid1), temp, wikidata_id1)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(geonameid1,ISO31661)            %>% group_by(geonameid1) %>% mutate(temp=ISO31661) %>% fill(temp) %>% mutate(ISO31661=ifelse(!is.na(geonameid1), temp, ISO31661)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(geonameid1,ISO31662)            %>% group_by(geonameid1) %>% mutate(temp=ISO31662) %>% fill(temp) %>% mutate(ISO31662=ifelse(!is.na(geonameid1), temp, ISO31662)) %>% dplyr::select(-temp) %>% ungroup() %>%

  
          #some of these names are dupes and we can group by that now and go down
          filter(!is.na(name1)) %>% #make sure again that all the names are the
          arrange(gid0,name1,geonameid0)        %>% group_by(gid0,name1) %>% mutate(temp=geonameid0) %>% fill(temp) %>% mutate(geonameid0=ifelse(!is.na(gid0), temp, geonameid0)) %>% dplyr::select(-temp) %>% ungroup() %>%
  
          arrange(gid0,name1,gid1)                %>% group_by(gid0,name1) %>% mutate(temp=gid1) %>% fill(temp) %>% mutate(gid1=ifelse(!is.na(gid1), temp, gid1)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid0,name1,geonameid0)                %>% group_by(gid0,name1) %>% mutate(temp=geonameid0) %>% fill(temp) %>% mutate(geonameid0=ifelse(!is.na(gid0), temp, geonameid0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid0,name1,geonameid1)                %>% group_by(gid0,name1) %>% mutate(temp=geonameid1) %>% fill(temp) %>% mutate(geonameid1=ifelse(!is.na(gid0), temp, geonameid1)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid0,name1,feature_code1)                %>% group_by(gid0,name1) %>% mutate(temp=feature_code1) %>% fill(temp) %>% mutate(feature_code1=ifelse(!is.na(gid0), temp, feature_code1)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid0,name1,wikidata_id0)                %>% group_by(gid0,name1) %>% mutate(temp=wikidata_id0) %>% fill(temp) %>% mutate(wikidata_id0=ifelse(!is.na(gid0), temp, wikidata_id0)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid0,name1,wikidata_id1)                %>% group_by(gid0,name1) %>% mutate(temp=wikidata_id1) %>% fill(temp) %>% mutate(wikidata_id1=ifelse(!is.na(gid0), temp, wikidata_id1)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid0,name1,ISO31661)                %>% group_by(gid0,name1) %>% mutate(temp=ISO31661) %>% fill(temp) %>% mutate(ISO31661=ifelse(!is.na(gid0), temp, ISO31661)) %>% dplyr::select(-temp) %>% ungroup() %>%
          arrange(gid0,name1,ISO31662)                %>% group_by(gid0,name1) %>% mutate(temp=ISO31662) %>% fill(temp) %>% mutate(ISO31662=ifelse(!is.na(gid0), temp, ISO31662)) %>% dplyr::select(-temp) %>% ungroup() %>%
  
          rename(admin1_name_clean=name1) %>% distinct() %>%
          mutate_if(is.numeric,as.character) %>% mutate_if(is.factor,as.character)
dim(admin1) #46,380 #43,710 #43828 #46,744
sapply(admin1, function(x) sum(is.na(x))) #That gets the missing down even more.

admin2 <- geonames_admin2 %>% left_join(admin1 %>% dplyr::select(-admin1_name_clean,-feature_code1) %>% distinct()) %>% 
          full_join(gadm2 ) %>% distinct() %>%
          arrange(geonameid0, geonameid1,geonameid2,gid0,gid1,gid2) %>% group_by(geonameid0,  geonameid1,  geonameid2 ) %>% fill(gid0,gid1,gid2) %>% ungroup() %>%
          arrange(gid0,gid1,gid2,geonameid0, geonameid1, geonameid2) %>% group_by(gid0,gid1,gid2 ) %>% fill(geonameid0,geonameid1,geonameid2, feature_code2) %>% ungroup() %>%
          distinct() %>%
          rename(admin2_name_clean=name2)
dim(admin2) #270,328

```



```{r}

#library(cld3)
#geonames_idtoname <- geonames_idtoname %>% mutate(lang= detect_language(name ) )
#sample <- geonames_idtoname %>% group_by(lang) %>% filter(row_number()<=10) %>% ungroup() %>% arrange(lang, name)
#nonlatin <- c( 'hy', 'bn', 'gu', 'hi', 'hy', 'iw', 'ka', 'km', 'kn', 'lo', 'ml', 'my', 'pa', 'ps', 'si', 'ta', 'te', 'th', 'ur','yi')
#geonames_idtoname_latin <- geonames_idtoname %>% filter(!lang %in% nonlatin)
#dim(geonames_idtoname_latin)

#We should kill off others that are nonenglish
#geonames_idtoname_latin_clean_unique <- geonames_idtoname_latin_clean %>% dplyr::select(geonameid, feature_code, name_clean) %>% distinct()
#dim(geonames_idtoname_latin_clean_unique) #1,024,714


dim(geonames_hierarchy_paths)
geonames_hierarchy_paths_labeled <- geonames_hierarchy_paths %>% 
                                    #left_join(geonames_idtoname %>% dplyr::select(V1=geonameid, name1=name, feature_code1=feature_code)) %>% 
                                    #left_join(geonames_idtoname %>% dplyr::select(V2=geonameid, name2=name, feature_code2=feature_code)) %>% #ignore anything above country
                                    left_join(geonames %>% dplyr::select(V3=geonameid, name3=name, feature_code3=feature_code)) %>%
                                    left_join(geonames %>% dplyr::select(V4=geonameid, name4=name, feature_code4=feature_code)) %>%
                                    left_join(geonames %>% dplyr::select(V5=geonameid, name5=name, feature_code5=feature_code)) %>%
                                    left_join(geonames %>% dplyr::select(V6=geonameid, name6=name, feature_code6=feature_code)) %>%
                                    left_join(geonames %>% dplyr::select(V7=geonameid, name7=name, feature_code7=feature_code)) %>%
                                    left_join(geonames %>% dplyr::select(V8=geonameid, name8=name, feature_code8=feature_code)) %>%
                                    left_join(geonames %>% dplyr::select(V9=geonameid, name9=name, feature_code9=feature_code)) %>%
                                    left_join(geonames %>% dplyr::select(V10=geonameid, name10=name, feature_code10=feature_code))

dim(geonames_hierarchy_paths_labeled)  #308,797



temp10 <- geonames_hierarchy_paths_labeled %>% filter(!is.na(V10)) %>%  mutate(geonameid=V10, name=paste(name3,name4,name5,name6,name7,name8,name9,name10,sep="_"), feature_code=feature_code10) %>% dplyr::select(geonameid, name, feature_code) %>% distinct()
temp9 <- geonames_hierarchy_paths_labeled %>% filter(!is.na(V9) & !is.na(V10)) %>%  mutate(geonameid=V9, name=paste(name3,name4,name5,name6,name7,name8,name9,sep="_"), feature_code=feature_code9) %>% dplyr::select(geonameid, name, feature_code) %>% distinct()
temp8 <- geonames_hierarchy_paths_labeled %>% filter(!is.na(V8) & !is.na(V9)) %>%  mutate(geonameid=V8, name=paste(name3,name4,name5,name6,name7,name8,sep="_"), feature_code=feature_code8) %>% dplyr::select(geonameid, name, feature_code) %>% distinct()
temp7 <- geonames_hierarchy_paths_labeled %>% filter(!is.na(V7) & !is.na(V8)) %>%  mutate(geonameid=V7, name=paste(name3,name4,name5,name6,name7,sep="_"), feature_code=feature_code7) %>% dplyr::select(geonameid, name, feature_code) %>% distinct()
temp6 <- geonames_hierarchy_paths_labeled %>% filter(!is.na(V6) & !is.na(V7)) %>%  mutate(geonameid=V6, name=paste(name3,name4,name5,name6,sep="_"), feature_code=feature_code6) %>% dplyr::select(geonameid, name, feature_code) %>% distinct()
temp5 <- geonames_hierarchy_paths_labeled %>% filter(!is.na(V5) & !is.na(V6)) %>%  mutate(geonameid=V5, name=paste(name3,name4,name5,sep="_"), feature_code=feature_code5) %>% dplyr::select(geonameid, name, feature_code) %>% distinct()
temp4 <- geonames_hierarchy_paths_labeled %>% filter(!is.na(V4) & !is.na(V5)) %>%  mutate(geonameid=V4, name=paste(name3,name4,sep="_"), feature_code=feature_code4) %>% dplyr::select(geonameid, name, feature_code) %>% distinct()
temp3 <- geonames_hierarchy_paths_labeled %>% filter(!is.na(V3) & !is.na(V3)) %>%  mutate(geonameid=V3, name=paste(name3,sep="_"), feature_code=feature_code3) %>% dplyr::select(geonameid, name, feature_code) %>% distinct()




admin1CodesASCII <- fread("/media/skynet2/905884f0-7546-4273-9061-12a790830beb/rwd_github_private/NESScovid19/data_temp/admin1CodesASCII.txt", sep="\t")
names(admin1CodesASCII) <- c('code', 'name', 'name ascii', 'geonameid')

admin2Codes <- fread("/media/skynet2/905884f0-7546-4273-9061-12a790830beb/rwd_github_private/NESScovid19/data_temp/admin2Codes.txt", sep="\t")
names(admin2Codes) <- c('code', 'name', 'name ascii', 'geonameid')

admin1CodesASCII_long <- admin1CodesASCII %>% dplyr::select(code1=code , name) %>% mutate(name=rex_clean(name))
admin2Codes_long <- admin2Codes %>% dplyr::select(code2=code , name) %>% mutate(name=rex_clean(name))

geonames_p %>% dplyr::select(geonameid,country_code,admin1,admin2)

countryInfo <- fread("/media/skynet2/905884f0-7546-4273-9061-12a790830beb/rwd_github_private/NESScovid19/data_temp/countryInfo.txt", sep="\t", skip=49)
names(countryInfo)[1] <- "ISO"

geonames_p <- geonames_p %>% 
              mutate(code1= paste0(country_code,".", admin1) ) %>%
              mutate(code1= paste0(country_code,".", admin1) ) %>%
              left_join(countryInfo %>% dplyr::select(country_code=ISO, admin0_name=Country))


```

Google maps

```{r}
#install.packages("mapsapi")
#library(mapsapi)
#doc = mp_geocode(addresses = "Tel-Aviv", key=) #couldn't get this to work with my api key. intentionally leaving it out here so I don't push it accidentally

```


# Introduction

Measurement is not reality
Correlation is not causation
Scale

ratios are the worst

How should we responsibly use COVID-19 counts? 

We want to know in a given population, how many people at some point have had COVID-19 and could have spread it to others. This is an unobserved latent variable.

Tests provide some information. 
There's some selection process by which a person from the population self selects and is selected to be tested. That test then has some true positive and true negative rate (and false positive and false negative rate).

Assume that more severe cases die. And more severe cases get tested.

Deaths provide some information. Assume a death implies a test with the same rates as the above. Might want to question that, there's some attribution process by which a death is either attributed to COVID or not. Some deaths are happening outside of the medical system and not getting tested or attributed to COVID.

So tests are at best a lower bound for how many in the population have the disease.

What do we learn from negative tests? Very crudely it could be how many people don't have COVID, which could be an upper bound on the number of infected. But it's out of date almost immediately, because all of those people could get infected tomorrow.




# LHS

## Mexico

https://www.reddit.com/r/datasets/comments/fykr5h/json_dataset_about_covid19_in_mexico/

## California Hosptilizations

https://github.com/CALmatters/covid-19-california-hospitalizations-data
https://public.tableau.com/profile/ca.open.data#!/vizhome/COVID-19PublicDashboard/Covid-19Hospitals

## ILILNet

#Can download state-week data here
https://gis.cdc.gov/grasp/fluview/fluportaldashboard.html

https://wwwn.cdc.gov/ILINet/

https://www.medrxiv.org/content/10.1101/2020.04.01.20050542v1

https://www.economist.com/graphic-detail/2020/04/11/why-a-study-showing-that-covid-19-is-everywhere-is-good-news?fsrc=scn%2Ftw%2Fte%2Fbl%2Fed%2Ffootprintsoftheinvisibleenemywhyastudyshowingthatcovid19iseverywhereisgoodnewsgraphicdetail&%3Ffsrc%3Dscn%2F=tw%2Fdc

## Bing

```{r}

library(jsonlite)
#library(rjson)
#tmp2 <- tempfile()
#curl_download("https://bing.com/covid/data", tmp2)
bing <- fromJSON("https://bing.com/covid/data")
#https://www.bing.com/covid/local/unitedstates

bing_df0 <- bind_rows(bing$areas) %>% mutate(admin0_name_original=displayName)
dim(bing_df0) #209  13

bing_df1 <- bind_rows(bing_df0$areas) %>% mutate(admin1_name_original=displayName) %>% left_join(bing_df0 %>% dplyr::select(parentId=id, admin0_name_original=displayName))
dim(bing_df1) #753  13

bing_df2 <- bind_rows(bing_df1$areas) %>% mutate(admin2_name_original=displayName) %>% 
            left_join(bing_df1 %>% dplyr::select(parentId=id, admin1_name_original=displayName)) %>%
            left_join(bing_df1 %>% dplyr::select(admin1_name_original,admin0_name_original))
dim(bing_df2) #2872   13

bing_long <- bind_rows(
          bing_df0 %>% dplyr::select(-areas),
          bing_df1 %>% dplyr::select(-areas),
          bing_df2 %>% dplyr::select(-areas)
) %>% 
  mutate(date_asdate = ymd(substring(lastUpdated,1,10))) %>%
  mutate(dataset="bing") %>% 
  
  mutate(admin0_name_clean=admin0_name_original %>% rex_clean()) %>%
  mutate(admin0_name_clean=str_replace(admin0_name_clean,"chinamainland","china")) %>%

  mutate(admin1_name_clean=admin1_name_original %>% rex_clean()) %>%

  
  mutate(admin2_name_clean=admin2_name_original %>% rex_clean()) %>%
  
  left_join(admin0 ) %>%
  left_join(admin1 )  %>%
  left_join(admin2 ) 


dim(bing_long)

#temp <- bing_long %>% dplyr::select(admin0_name_clean,admin1_name_clean,admin2_name_clean,gid0,gid1,gid2) %>% distinct()

```

## WHO

```{r}
WHO <- read_csv(url("https://raw.githubusercontent.com/datasets/covid-19/master/data/countries-aggregated.csv")) 

who_long <- WHO %>%
            mutate(dataset="bing") %>%
            mutate(admin0_name_original=Country) %>%
            mutate(date_asdate = ymd(Date)) %>% 
            rename(confirmed=Confirmed  , deaths=Deaths)  %>%
  
             mutate(admin0_name_clean=admin0_name_original %>% rex_clean()) %>%
              left_join(admin0 ) %>%
              left_join(admin1 )  %>%
              left_join(admin2 ) 

```

## CSSEGISandData

```{r, echo=F, message=FALSE, results = FALSE, warning=FALSE}

#https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/
CSSE_confirmed_us      <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_US.csv"))
CSSE_confirmed_global  <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv"))

CSSE_deaths_us      <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_US.csv"))
CSSE_deaths_global  <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"))

CSSE_confirmed_us_long <- pivot_longer(CSSE_confirmed_us, names_to = "date", cols = ends_with("20"), values_to = "confirmed")
CSSE_confirmed_global_long <- pivot_longer(CSSE_confirmed_global, names_to = "date", cols = ends_with("20"), values_to = "confirmed")

CSSE_deaths_us_long <- pivot_longer(CSSE_deaths_us, names_to = "date", cols = ends_with("20"), values_to = "deaths")
CSSE_deaths_global_long <- pivot_longer(CSSE_deaths_global, names_to = "date", cols = ends_with("20"), values_to = "deaths")

CSSE_us_long <- CSSE_confirmed_us_long %>% full_join(CSSE_deaths_us_long) %>% mutate(admin0_name_original="United States") %>% mutate(admin1_name_original=Province_State) %>% mutate(admin2_name_original=Admin2)
CSSE_global_long <- CSSE_confirmed_global_long %>% full_join(CSSE_deaths_global_long) %>% mutate(admin0_name_original=`Country/Region`) %>% mutate(admin1_name_original=`Province/State`)

CSSE_long <- bind_rows(CSSE_us_long, CSSE_global_long) %>% 
              mutate(dataset="CSSE") %>%
              mutate(date_asdate = mdy(str_replace(date,"20$","2020"))) %>%

              mutate(admin0_name_clean=admin0_name_original %>% rex_clean())  %>%
              left_join(admin0 ) %>%
              left_join(admin1 ) %>%
              left_join(admin2 ) 

```


## NYT


```{r}
#https://www.nytimes.com/article/coronavirus-county-data-us.html
#https://github.com/nytimes/covid-19-data
nytimes <- read_csv(url("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-counties.csv")) #

nytimes_long <- nytimes %>%
                mutate(date_asdate = ymd(date)) %>% 
                rename(confirmed=cases) %>%
                mutate(dataset="nyt") %>%
                mutate(admin0_name_original="United States") %>%
                mutate(admin1_name_original=state) %>%
                mutate(admin2_name_original=county)  %>%

                mutate(admin0_name_clean=admin0_name_original %>% rex_clean()) %>%
                mutate(admin0_name_clean=str_replace(admin0_name_clean,"chinamainland","china")) %>%
              
                mutate(admin1_name_clean=admin1_name_original %>% rex_clean()) %>%
                mutate(admin1_name_clean= ifelse(!is.na(admin1_name_clean) & admin1_name_clean !='', 
                                          paste0(admin0_name_clean,"_",admin1_name_clean),
                                          NA)
                       ) %>%
                
                mutate(admin2_name_clean=admin2_name_original %>% rex_clean()) %>%
                mutate(admin2_name_clean= ifelse(!is.na(admin2_name_clean) & admin2_name_clean !='', 
                                          paste0(admin1_name_clean,"_",admin2_name_clean),
                                          NA)
                       )  %>%
              left_join(admin0 ) %>%
              left_join(admin1 ) %>%
              left_join(admin2 ) 

```

### Covidtracking.com

```{r}
#https://covidtracking.com/about-data
"If you are calculating positive rates, it should only be with states that have an A grade. And be careful going back in time because almost all the states have changed their level of reporting at different times."

#The data contain the u.s. and the states too
#FIPS the first two digits are the state
#All 0 is the U.S.
#
#https://covidtracking.com/api
covidtracking <- read_csv(url("https://covidtracking.com/api/states/daily.csv"))
dim(covidtracking) #1653   25
covidtracking_t <- t(covidtracking)

covidtracking_long <- covidtracking %>%
                      mutate(date_asdate = ymd(date)) %>% 
                      rename(state_abbr=state) %>%
                      left_join(state_codes) %>% 
                      dplyr::select(date_asdate, state_name, state_abbr, positive, negative, death) %>%
                      mutate(admin0_name_original="United States") %>%
                      mutate(admin1_name_original=state_name)  %>%
                      left_join(admin0 ) %>%
                      left_join(admin1 ) %>%
                      left_join(admin2 ) 

```

### wikipedia

```{r}

#https://rviews.rstudio.com/2020/03/05/covid-19-epidemiology-with-r/
library(rvest)
wp_page_url = "https://en.wikipedia.org/wiki/COVID-19_testing"
testing_webpage <- read_html(wp_page_url)

# parse the web page and extract the data from the eighth
# table
testing_tables <- testing_webpage %>% html_nodes("table") %>%  html_table(fill = TRUE)
lapply(testing_tables, colnames)

wikipedia_tests <- testing_tables[[4]] 

data(codelist)
countries_for_matching <- codelist %>% unlist() %>% unique() %>% sort()
wikipedia_tests_long <- wikipedia_tests %>% 
                        mutate(date_asdate = dmy(paste( `As of`, ", 2020" )   )) %>% 
                        mutate(tests=str_replace(Tests, ",","")) %>%
                        mutate(confirmed=str_replace(Positive, ",","")) %>% 
                        rename(text=`Country or region`) %>%
                        mutate(text=trimws(str_replace(text,"\\(unofficial\\)",""))) %>%
                        mutate(is_country = text %in% countries_for_matching) %>%
                        mutate(admin0_name_original = ifelse(is_country,text, NA  )) %>%
                        fill(admin0_name_original) %>%
                        mutate(admin1_name_original = ifelse(!is_country,text, NA  )   ) 
  
```
metabiota.com

```{r}

metabiota <- read_csv("/home/skynet2/Downloads/data_ncov2019.csv")
dim(metabiota) #605848

table(metabiota$OUTCOME)
table(metabiota$CUMULATIVE_FLAG)

#cities look broken with just a flat number of 1 or 2 "Ho Chi Minh City"

metabiota_confirmed <- metabiota %>% filter(CUMULATIVE_FLAG==T) %>% filter(OUTCOME=="CASE") %>% filter(CONFIRM_STATUS=="CONFIRMED") %>% 
                       filter( DATE_LOW==DATE_HIGH) %>%
                       mutate(composite_source = SOURCE=="Metabiota Composite Source") %>%
                       distinct() %>%
                       arrange(AL0_NAME,AL1_NAME,AL2_NAME ,AL3_NAME, LOCALITY_NAME, DATE_LOW, -composite_source) %>%
                       group_by(AL0_NAME,AL1_NAME,AL2_NAME ,AL3_NAME, LOCALITY_NAME, DATE_LOW) %>%
                       filter(row_number()==1) %>%
                       ungroup() %>%
                       dplyr::select(date=DATE_LOW,AL0_NAME,AL1_NAME,AL2_NAME ,AL3_NAME,LOCALITY_NAME,confirmed=VALUE) 

metabiota_deaths <- metabiota %>% filter(CUMULATIVE_FLAG==T) %>% filter(OUTCOME=="DEATH") %>% filter(CONFIRM_STATUS=="CONFIRMED") %>% 
                       filter( DATE_LOW==DATE_HIGH) %>%
                       mutate(composite_source = SOURCE=="Metabiota Composite Source") %>%
                       distinct() %>%
                       arrange(AL0_NAME,AL1_NAME,AL2_NAME ,AL3_NAME, LOCALITY_NAME, DATE_LOW, -composite_source) %>%
                       group_by(AL0_NAME,AL1_NAME,AL2_NAME ,AL3_NAME, LOCALITY_NAME, DATE_LOW) %>%
                       filter(row_number()==1) %>%
                       ungroup() %>%
                       dplyr::select(date=DATE_LOW,AL0_NAME,AL1_NAME,AL2_NAME ,AL3_NAME,LOCALITY_NAME,deaths=VALUE) 

metabiota_long <- metabiota_confirmed %>% 
                  full_join(metabiota_deaths) %>%
                  group_by(AL0_NAME,AL1_NAME,AL2_NAME ,AL3_NAME, LOCALITY_NAME) %>%
                  filter(min(confirmed)!=max(confirmed)) %>% #require some variation
                  ungroup() %>%
                  rename(admin0_name_original=AL0_NAME,
                         admin1_name_original=AL1_NAME,
                         admin2_name_original=AL2_NAME,
                         admin3_name_original=LOCALITY_NAME
                         ) %>%
                  dplyr::select(-AL3_NAME) %>%

                  mutate(admin0_name_clean=admin0_name_original %>% rex_clean()) %>%
                  mutate(admin0_name_clean=str_replace(admin0_name_clean,"chinamainland","china")) %>%
                
                  mutate(admin1_name_clean=admin1_name_original %>% rex_clean()) %>%

                  mutate(admin2_name_clean=admin2_name_original %>% rex_clean()) %>%

                  mutate(admin3_name_clean=admin3_name_original %>% rex_clean()) %>%
                      left_join(admin0 ) %>%
                      left_join(admin1 ) %>%
                      left_join(admin2 ) 



temp <- metabiota_long %>% dplyr::select(admin0_name_clean,admin1_name_clean,admin2_name_clean,admin3_name_clean,
                                         gid0,gid1,gid2,gid3) %>% distinct()


#Drop any with no variation

#https://data.humdata.org/dataset/2019-novel-coronavirus-cases
#Spatiotemporal data for 2019-Novel Coronavirus Covid-19 Cases and deaths
#This dataset is part of COVID-19 Pandemic
#Data Overview
#This repository contains spatiotemporal data from many official sources for 2019-Novel Coronavirus beginning 2019 in Hubei, China ("nCoV_2019")
#You may not use this data for commercial purposes. If there is a need for commercial use of the data, please contact Metabiota at info@metabiota.com to obtain a commercial use license.

```

All wikipedia covid pages

```{r}
library(countrycode)
data(codelist)
countries_for_matching <- codelist %>% unlist() %>% unique() %>% sort()

library(rvest)

#link has
"2020_coronavirus_pandemic_in_"
url <- "https://en.wikipedia.org/wiki/2019%E2%80%9320_coronavirus_pandemic_by_country_and_territory"

#the 5000 is to say don't limit number of hits on the page, 5k 
url <- "https://en.wikipedia.org/w/index.php?title=Special:Search&limit=5000&offset=0&profile=default&search=%22coronavirus+pandemic+in%22&advancedSearch-current={}&ns0=1" #here's a search querry that captures both countries and places
wikipedia_by_country_webpage <- read_html(url)

links <- wikipedia_by_country_webpage %>% html_nodes("a") %>% html_attr(c('href'))
titles <- wikipedia_by_country_webpage %>% html_nodes("a") %>% html_attr(c('title')) 
text <- wikipedia_by_country_webpage %>% html_nodes("a") %>% html_text() 
wikipedia_by_country_links <- data.frame(link=paste0("https://en.wikipedia.org/",links) , 
                                         title=titles,
                                         text=text) %>% 
                              filter(!is.na(title)) %>% 
                              filter(!str_detect(title,"Template")) %>% 
                              filter(!str_detect(title,"Timeline")) %>% 
                              filter(!str_detect(title,"Chronology of the|Economic impact|Responses to|page does not exist")) %>% 
  
                              filter(str_detect(title,"coronavirus pandemic in")) %>%
                              mutate(is_country = text %in% countries_for_matching) %>%
                              mutate_if(is.factor, as.character) %>%
                              mutate(place=str_replace(title, ".*coronavirus pandemic in ","")) %>%
                              distinct()
dim(wikipedia_by_country_links) #345   4

tables_keep_list <- list()
for(i in 1:nrow(wikipedia_by_country_links)){
  temp_place=wikipedia_by_country_links$place[i]
  print(temp_place)
  temp_html <- read_html(wikipedia_by_country_links$link[i])
  temp_tables <- temp_html  %>% html_nodes("table") %>%  html_table(fill = TRUE, header=F) 
  
  test <- temp_tables[[10]] %>%  html_table(fill = TRUE, header=F) 
  test2 <- temp_tables[[10]] %>%  html_table(fill = F, header=F) #nope still throws an error
  
  library(htmltab) ; #install.packages('htmltab')
  url <- wikipedia_by_country_links$link[i]
  ukLang <- htmltab(doc = url, which = 1)
  ukLang <- htmltab(doc = url, which = 10, complementary=F, headerSep="_")
  
  head(ukLang)

  
  temp_tables_df <- lapply(temp_tables, FUN=function(x) { 
                        tryCatch({
                           html_table(x,fill = TRUE, header=F)} ,
                           error = function(e) return(data.frame()) 
                        )   } )  #the one I want is throwing an error
  
  condition <- which(sapply(temp_tables_df, ncol)>3 & sapply(temp_tables_df, nrow)>3)
  temp_tables_deaths <- temp_tables_df[condition]

  #do any of these tables have the word death
  condition <- which(  sapply(temp_tables_deaths, FUN=function(x) sum(str_detect(unique(unlist(x)), "death|Death"), na.rm=T)  )>0)
  temp_tables_deaths <- temp_tables_deaths[condition]

  condition <- which(  sapply(temp_tables_deaths, FUN=function(x) sum(str_detect(unique(unlist(x)), "Data \\(templates\\)|Medical professional|SARS-CoV-2 \\(virus\\) COVID-19 \\(disease\\)"), na.rm=T)  )==0)
  temp_tables_deaths <- temp_tables_deaths[condition]
  
  #lapply(temp_tables_deaths, dim)
  #lapply(temp_tables_deaths, colnames)

  tables_keep_list[[temp_place]] <- temp_tables_deaths
  temp1 <- temp_tables_deaths[[1]]
  temp2 <- temp_tables_deaths[[2]]
  temp3 <- temp_tables_deaths[[3]]
  temp4 <- temp_tables_deaths[[4]]
  
}



```


# RHS

## Testing

### ourworldindata.org

```{r}

#https://drive.google.com/drive/folders/1HPzXon49teN-kMQlY1ry9rh2eq-TyGQI
#https://ourworldindata.org/covid-testing
#on how to reformat the url for straight downloading
#https://gist.github.com/tanaikech/f0f2d122e05bf5f971611258c22c110f
library(googledrive)
library(curl)
tmp <- tempfile()
#curl_download("https://drive.google.com/open?id=18QE3wScRXL-ARIaBl6yh7xUVNlnitvW_", tmp)


#There's also a github repo
#
worldindata_github <- read_csv("https://raw.githubusercontent.com/owid/covid-19-data/master/public/data/testing/covid-testing-all-observations.csv") 

curl_download("https://drive.google.com/uc?export=download&id=18QE3wScRXL-ARIaBl6yh7xUVNlnitvW_", tmp)
worldindata_googledrive <- read_csv(tmp) 

dim(worldindata_github)
dim(worldindata_googledrive) #The github one is longer

worldindata_long <- worldindata_github %>%
                    mutate(date_asdate = ymd(Date)) %>%  
                    separate(Entity, c("admin0_name_original", "note"), sep="-") %>%
                    mutate(admin0_name_original=trimws(admin0_name_original)) %>%
                    rename(tests=`Cumulative total`) %>%
                    mutate(admin0_name_clean=admin0_name_original %>% rex_clean()) %>%
                    left_join(admin0 %>% dplyr::select(geonameid0=geonameid,gid0=gid,admin0_name_clean=name))

```




## Demographics

### U.S. County Demographics

```{r}

#library(R0)  # consider moving all library commands to top -- this one was in a loop below
#Until the U.S. states one goes live have to pull it from here
#Codebook
#https://github.com/JieYingWu/COVID-19_US_County-level_Summaries/blob/master/data/list_of_columns.md
counties <- read_csv(url("https://raw.githubusercontent.com/JieYingWu/COVID-19_US_County-level_Summaries/master/data/counties.csv")) #using the archived copy from today because they haven't posted the 
counties_t <- t(counties)

counties_1 <- counties %>%
                      filter(as.numeric(substring(FIPS,3,5))==0 & Area_Name!="United States") %>%
                      mutate(admin0_name_original="United States") %>%
                      mutate(admin1_name_original=Area_Name) 
counties_2 <- counties %>% filter(as.numeric(substring(FIPS,3,5))>0 & Area_Name!="United States") %>% 
                      left_join(state_codes %>% rename(State=state_abbr)) %>%
                      mutate(admin0_name_original="United States") %>%
                      mutate(admin1_name_original=state_name)  %>%
                      mutate(admin2_name_original=Area_Name) 

counties_long <- bind_rows(counties_1,counties_2) %>%
                    mutate(admin0_name_clean=admin0_name_original %>% rex_clean()) %>%
                      left_join(admin0 ) %>%
                      left_join(admin1 ) %>%
                      left_join(admin2 ) 


```

## 
The international political economy data resource
https://link.springer.com/article/10.1007/s11558-017-9285-0

```{r}
tmp2 <- tempfile()
temp_url <- "https://dataverse.harvard.edu/api/access/datafile/:persistentId?persistentId=doi:10.7910/DVN/X093TV/XHEWU3"
curl_download(temp_url, tmp2)
load(tmp2) #the object's name is ipe_full
glimpse(ipe_full)
#$ country                     <chr> "United States of America", "United States of America", "United States of America", "United States of America", "United States of America", "United States of America", "United States of America", "United States of America", "United States of
#$ year                        <dbl> 1800, 1801, 1802, 1803, 1804, 1805, 1806, 1807, 1808, 1809, 1810, 1811, 1812, 1813, 1814, 1815, 1816, 1817, 1818, 1819, 1820, 1821, 1822, 1823, 1824, 1825, 1826, 1827, 1828, 1829, 1830, 1831, 1832, 1833, 1834, 1835, 1836, 1837, 1838, 1839, 1
#$ gwno                        <dbl> 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2
#$ ccode                       <dbl> 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2
#$ ifscode                     <dbl> 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 111, 1
#$ ifs                         <chr> "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "USA", "US
#$ gwabbrev 

ipe_long <- ipe_full %>% 
  group_by(country) %>% filter(year==max(year)) %>% ungroup()
#the whole dataset ends in 2017 and a lot of these values aren't available that recently which is interesting

#codebook
#https://dataverse.harvard.edu/file.xhtml?persistentId=doi:10.7910/DVN/X093TV/OIB5GS&version=3.0

ipe_long <- ipe_full %>%
            mutate_if(is.numeric,as.character, is.factor, as.character) %>% #https://stackoverflow.com/questions/58124530/pivot-longer-with-multiple-classes-causes-error-no-common-type
            pivot_longer( names_to = "variable", cols = onset2_AO:english_off_USA_CE, values_to = "value", values_ptypes = list(val = 'character')) %>% filter(!is.na(value))  %>% 
            group_by(country, variable) %>% 
            filter(year==max(year)) %>% 
            ungroup()  %>%
            mutate(admin0_name_clean=country %>% rex_clean()) %>%
            left_join(admin0 %>% dplyr::select(geonameid0=geonameid,gid0=gid,admin0_name_clean=name))

```


```{r}
#World Development Indicators
#http://datatopics.worldbank.org/world-development-indicators/
#csv bulk zip download
#http://databank.worldbank.org/data/download/WDI_csv.zip


WDIData <- read_csv("/media/skynet2/905884f0-7546-4273-9061-12a790830beb/rwd_github_private/NESScovid19/data_temp/WDIData.csv")

WDIData_long <- WDIData %>%
                mutate_if(is.numeric,as.character, is.factor, as.character) %>% #https://stackoverflow.com/questions/58124530/pivot-longer-with-multiple-classes-causes-error-no-common-type
                pivot_longer( names_to = "year", cols = `1960`:X65, values_to = "value", values_ptypes = list(val = 'character')) %>% filter(!is.na(value))  %>% 
                group_by(`Country Name`, `Indicator Name`) %>% 
                filter(year==max(year)) %>% 
                ungroup() 
                

colnames(WDIData_long) <- colnames(WDIData_long) %>% str_replace_all(" ","_") %>% tolower()

WDIData_long <- WDIData_long %>%
                mutate(indicator_name=indicator_name%>% str_replace_all(" ","_") %>% tolower()) %>%
                rename(admin0_name_original=country_name) %>%
                mutate(admin0_name_clean=admin0_name_original %>% rex_clean()) %>%
                left_join(admin0 %>% dplyr::select(geonameid0=geonameid,gid0=gid,admin0_name_clean=name))

temp <- WDIData_long %>% count(indicator_name)

```



## Mobility

### Google Mobility Data

```{r}
#Google mobility daily data from the trend lines
#https://github.com/nacnudus/google-location-coronavirus
#only at the country level though
google_mobility_timelines <- read_tsv("https://raw.githubusercontent.com/nacnudus/google-location-coronavirus/master/2020-03-29.tsv")

```

```{r}

#Mobility datga
google_mobility_us <- read_csv(url("https://raw.githubusercontent.com/ActiveConclusion/COVID19_mobility/master/mobility_report_US.csv")) #
google_mobility_regions <- read_csv(url("https://raw.githubusercontent.com/ActiveConclusion/COVID19_mobility/master/mobility_report_regions.csv")) #

google_mobility_us_long <- google_mobility_us %>%
                   mutate(date_asdate = ymd(Date)) %>%
                    mutate(admin0_name_original="United States") %>%
                    mutate(admin1_name_original=State)  %>%
                    mutate(admin2_name_original=Region) %>%
                    mutate(admin2_name_original=ifelse(admin2_name_original=="Total",NA, admin2_name_original))

google_mobility_regions_long <- google_mobility_regions %>%
                          mutate(date_asdate = ymd(Date)) %>%
                          mutate(admin0_name_original=Country) %>%
                          mutate(admin1_name_original=Region)  %>%
                          mutate(admin1_name_original=ifelse(admin1_name_original=="Total",NA, admin1_name_original))  

google_mobility_long <- 
                  bind_rows(google_mobility_us_long,
                            google_mobility_regions_long) %>%
                  rename(google_retail= `Retail & recreation`,
                         google_grocery=`Grocery & pharmacy`,
                         google_park= Parks,
                         google_transit=`Transit stations`,
                         google_workplace=Workplaces,
                         google_residential=Residential) %>% 
                  distinct() %>%
                mutate(admin0_name_clean=admin0_name_original %>% rex_clean()) %>%
                left_join(admin0 %>% dplyr::select(geonameid0=geonameid,gid0=gid,admin0_name_clean=name))
  
```


NYT state order issued

```{r}
#https://www.nytimes.com/interactive/2020/us/coronavirus-stay-at-home-order.html
```

# Munging

```{r, eval=F}

places <- bind_rows(
            google_mobility_long %>% dplyr::select(admin0_name_original, admin1_name_original, admin2_name_original),
            counties_long %>% dplyr::select(admin0_name_original, admin1_name_original, admin2_name_original, fips=FIPS) %>% mutate(fips=as.character(fips)),
            worldindata_long %>% dplyr::select(admin0_name_original),
            covidtracking_long %>% dplyr::select(admin0_name_original, admin1_name_original),
            nytimes_long %>% dplyr::select(admin0_name_original, admin1_name_original, admin2_name_original, fips),
            CSSE_long %>% dplyr::select(admin0_name_original, admin1_name_original, admin2_name_original,fips=FIPS) %>% mutate(fips=as.character(fips)),
            who_long %>% dplyr::select(admin0_name_original),
            bing_long %>% dplyr::select(admin0_name_original, admin1_name_original, admin2_name_original),
            wikipedia_tests_long %>% dplyr::select(admin0_name_original, admin1_name_original),
            metabiota_long %>% dplyr::select(admin0_name_original, admin1_name_original, admin2_name_original,admin3_name_original),
            WDIData_long %>% dplyr::select(admin0_name_original)
) %>%
  dplyr::select(admin0_name_original, admin1_name_original, admin2_name_original,admin3_name_original,fips) %>% 
  distinct() %>%
  arrange(admin0_name_original, admin1_name_original, admin2_name_original) %>%
  mutate(admin0_name_clean=admin0_name_original %>% rex_clean()) %>%
  mutate(admin1_name_clean=admin1_name_original %>% rex_clean()) %>%
  mutate(admin2_name_clean=admin2_name_original %>% rex_clean()) %>%
  mutate(admin3_name_clean=admin3_name_original %>% rex_clean()) %>%
  left_join(gadm_long %>% dplyr::select(gadm0,admin0_name_clean) %>% na.omit() ) %>%
  left_join(gadm_long %>% dplyr::select(gadm0,gadm1,admin1_name_clean) %>% na.omit() ) %>%
  left_join(gadm_long %>% dplyr::select(gadm0,gadm1,gadm2,admin2_name_clean) %>% na.omit())
  
dim(places) #12203     4


places <- all_long %>% dplyr::select(country,state) %>% distinct() %>% mutate(search=paste0(state,", ", country ))  %>% mutate(search= ifelse(is.na(state) | state=="none", country, state ) )
library(WikidataR)
wiki_searches <- list()
for(q in places$search){
  print(q)
  try({
    #wiki <- find_item("Bexas County")
    wiki <- find_item(q)
    temp <- as.data.frame(wiki[[1]])
    temp$search <- q
    wiki_searches[[q]] <- temp
  })
}
wiki_searches_df <- bind_rows(wiki_searches)


```


# Points


# Comparison by source

# 

# Case Fatality Rates

# Case Fatality Rates as a function of Cases

# Case Fataility Rates as a function of cases and testing

# Case Fataility Rates as a function of cases and testing and Time

# Rates of Change and R0

# Crests 

# Residuals

What areas have more or fewer cases/deaths than we would expect?


```{r}

#has new york city as a single entitiy but not the constituent counties which is frustrating

library(strucchange) ; #install.packages('strucchange')
temp <- nytimes_long %>% arrange(date_asdate) %>% filter(county %in% "Bexar") %>% 
  mutate(confirmed_log=log(confirmed+1)) %>%
  mutate(date_rank= rank(date_asdate))  
bp <- breakpoints(confirmed_log ~ 1, data=temp)
bp <- breakpoints(confirmed_log ~ 1 + date_rank, data=temp)
temp %>% ggplot() + geom_point(aes(x=rank(date_asdate), y=confirmed_log)) + geom_vline(xintercept=bp$breakpoints)
coef(bp)


temp <- nytimes_long %>% arrange(date_asdate) %>% filter(county %in% "New York City") %>% 
  mutate(confirmed_log=log(confirmed+1)) %>%
  mutate(t= rank(date_asdate))  
bp <- breakpoints(confirmed_log ~ 1, data=temp)
bp <- breakpoints(confirmed_log ~ 1 + t, data=temp)

tmin <- min(temp$t)
tmax <- max(temp$t)
c(tmin, bp$breakpoints, tmax)


cdf <- data.frame(
  t= c(1,bp$breakpoints), 
  t_slope= coef(bp)[,2]
)

temp <- temp %>% 
  mutate(y_hat = fitted.values(bp)) %>%
  left_join(cdf) %>% 
  fill(t_slope) %>%
  mutate(t_slope_percent_change = round((exp(t_slope)-1)*100,2))

temp %>% ggplot() +
  geom_point(aes(x=rank(date_asdate), y=confirmed_log)) + 
  geom_line(aes(x=rank(date_asdate), y=y_hat)) + 
  geom_vline(xintercept=bp$breakpoints)
```

```{r}

temp_list <- list()
for(q in places$place){
  print(q)
  temp <- NULL
  temp <- nytimes_long %>% 
    arrange(date_asdate) %>% 
    filter(place %in% q) %>% 
    mutate(confirmed_log=log(confirmed+1)) %>%
    mutate(t= rank(date_asdate))  
  if( nrow(temp)==0 ) {print("error"); break}
  
  #bp <- breakpoints(confirmed_log ~ 1, data=temp)
  bp <- NULL
  lm1 <- NULL
  y_hat <- NA
  cdf <- NULL
  try({
    #if it fails fall back to just a lm
    lm1 <- lm(confirmed_log ~ 1 + t, data=temp)
    
    cdf <- data.frame(
      t= 1, 
      t_slope= coef(lm1)[2],
      t_slope_break=0
    )
    y_hat=fitted.values(lm1)
  })
  
  try({
    bp <- breakpoints(confirmed_log ~ 1 + t, data=temp)
    
    cdf <- data.frame(
      t= c(1,bp$breakpoints), 
      t_slope= coef(bp)[,2],
      t_slope_break=1
    )
    y_hat=fitted.values(bp)
  })
  
  try({
    temp <- temp %>% 
      mutate(y_hat = y_hat) %>%
      left_join(cdf) %>% 
      fill(t_slope) %>%
      mutate(t_slope_percent_change = round((exp(t_slope)-1)*100,2))
    
    temp_list[[as.character(q)]] <- temp
  })
  #if( is.na( temp_list[[as.character(q)]]$y_hat) ) {print("error"); break}
}
#"13055"
temp_df <- bind_rows(temp_list)
dim(temp_df)

temp_list[["New York_New York City_NA"]]


```

```{r}

temp_df_max <- temp_df %>% group_by(fips) %>% filter(date_asdate==max(date_asdate)) %>% ungroup()

hist(temp_df_max$t_slope_percent_change, breaks=50)

temp_df_max %>% ggplot() + geom_density(aes(x=t_slope_percent_change))

```

```{r}
temp_df %>% 
  head(1000) %>%
  ggplot() +
  geom_line(aes(x=date_asdate,
                y=t_slope_percent_change,
                color=fips))  + theme(legend.position = "none")

```

```{r}
temp_df %>%
  filter(place %in% "New York_New York City_NA")  %>% 
  mutate(date_asdate_rank=rank(date_asdate)) %>%
  ggplot() +
  geom_point(aes(x=date_asdate,y=t_slope_percent_change))


temp_df %>%
  filter(place %in% "New York_New York City_NA")  %>% 
  ggplot() +
  geom_point(aes(x=date_asdate,y=confirmed_log)) +
  geom_line(aes(x=date_asdate,y=y_hat)) +
  #geom_point(aes(x=date_asdate,y=t_slope_percent_change))
  
  temp_df %>%
  filter(place %in% "Texas_Bexar_48029")  %>% 
  ggplot() +
  geom_point(aes(x=date_asdate,y=confirmed_log)) +
  geom_line(aes(x=date_asdate,y=y_hat))

library(gghighlight)
temp_df %>%
  filter(place %in% c("New York_New York City_NA","Texas_Bexar_48029","California_San Diego_06073","Florida_St. Lucie_12111") ) %>% 
  ggplot(aes(x=date_asdate, color=place)) +
  geom_point(aes(y=confirmed_log)) +
  geom_line(aes(y=y_hat)) +
  gghighlight(#prefered_label %in% c("Washington, US","Italy","China") , #"New York, US" #, "US"
    label_params =
      list(
        size = 3,
        segment.alpha=0)
  ) +
  theme_bw()

library(gghighlight)
temp_df %>%
  filter(t_slope_percent_change>1 & confirmed>20 ) %>% 
  mutate(y_hat_exp=exp(y_hat) ) %>% 
  
  ggplot(aes(x=date_asdate, color=place)) +
  geom_point(aes(y=confirmed_log)) +
  geom_line(aes(y=y_hat)) +
  gghighlight(place %in% c("New York_New York City_NA","Texas_Bexar_48029","California_San Diego_06073","Florida_St. Lucie_12111") , 
              label_params =
                list(
                  size = 3,
                  segment.alpha=0)
  ) +
  theme_bw() + ylim(3,11.5)

library(scales)
library(gghighlight)
temp_df %>%
  filter(t_slope_percent_change>1 & confirmed>20 ) %>% 
  mutate(y_hat_exp=exp(y_hat) ) %>% 
  
  ggplot(aes(x=date_asdate, color=place)) +
  geom_point(aes(y=confirmed)) +
  geom_line(aes(y=y_hat_exp)) +
  gghighlight(place %in% c("New York_New York City_NA","Texas_Bexar_48029","California_San Diego_06073","Florida_St. Lucie_12111") , 
              label_params =
                list(
                  size = 3,
                  segment.alpha=0)
  ) +
  theme_bw() + scale_y_log10(labels = comma_format()) #+ ylim(10, 100000)


temp_df %>%
  filter(t_slope_percent_change>1 & confirmed>=20 ) %>% 
  mutate(y_hat_exp=exp(y_hat) ) %>% 
  
  ggplot(aes(x=days_since_20_confirmed, color=place)) +
  geom_point(aes(y=confirmed)) +
  geom_line(aes(y=y_hat_exp)) +
  gghighlight(place %in% c("New York_New York City_NA","Texas_Bexar_48029","California_San Diego_06073","Florida_St. Lucie_12111") , 
              label_params =
                list(
                  size = 3,
                  segment.alpha=0)
  ) +
  theme_bw() + scale_y_log10(labels = comma_format()) #+ ylim(10, 100000)




```

Ok so we put slope at days since 20 confirmed on the left hand side, and put other covariates on the rhs


```{r}


lhs_20 <- temp_df %>% 
  filter(t_slope_percent_change>1 & confirmed>=20 ) %>% 
  mutate(y_hat_exp=exp(y_hat) ) %>%
  left_join( state_codes %>% dplyr::select(state=state_name, state_abbr ) )
dim(lhs_20)

dim(covidtracking)

contemporary_us  <- us_counties()
rhs_mobility <- mobility %>% 
  mutate(Region=str_replace(Region," County","")) %>%
  left_join(contemporary_us %>% 
              mutate(fips=paste0(statefp , countyfp))  %>% as.data.frame() %>% 
              dplyr::select(fips, State=state_name , Region=name  ) 
  ) %>%
  rename(google_retail= `Retail & recreation`,
         google_grocery=`Grocery & pharmacy`,
         google_park= Parks,
         google_transit=`Transit stations`,
         google_workplace=Workplaces,
         google_residential=Residential) %>% 
  distinct()


rhs_covidtracking <- covidtracking %>%
  mutate(date_asdate = ymd(date)) %>% 
  dplyr::select(date_asdate, state_abbr=state, state_test_positive=positive, state_test_negative=negative) %>%
  mutate( state_test = state_test_positive + state_test_negative) %>% 
  left_join(statepop  %>% dplyr::select(state_abbr=abbr, pop_2015) ) %>%
  mutate( state_test_percap = state_test/pop_2015) %>% 
  distinct()



rhs_counties <- counties %>% dplyr::select(fips=FIPS, 
                                    TOT_MALE, TOT_FEMALE,
                                    doctors_per_cap=`Active Physicians per 100000 Population 2018 (AAMC)`,
                                    popdensity=`Density per square mile of land area - Population`,
                                    area=`Area in square miles - Total area`,
                                    Median_Household_Income_2018,
                                    Total_age65plus,
                                    WA_MALE,	#White alone male population
                                    WA_FEMALE,	#White alone female population
                                    hospitals=`Total Hospitals (2019)`
) %>% 
  mutate(pop=TOT_MALE+TOT_FEMALE) %>% mutate(pop_perc_male = TOT_MALE/pop) %>% 
  mutate(pop_over65_perc=Total_age65plus/pop) %>%
  mutate(pop_nonwhite_perc= (pop-(WA_MALE+WA_FEMALE))/pop  ) %>%
  
  distinct()

xy_all <- lhs_20 %>% filter(county!="Unknown") %>%
  mutate(date_numeric=as.numeric(date_asdate)) %>% 
  left_join(rhs_covidtracking)  %>% 
  left_join(rhs_counties) %>% 
  left_join(rhs_mobility)
dim(xy_all)
glimpse(xy_all)

xy_all_cross_section <- xy_all %>% group_by(place) %>% filter(date_numeric==max(date_numeric)) %>% filter(!is.na(fips))  %>% ungroup() %>% as.data.frame()
dim(xy_all_cross_section)

xy_all_cross_section$pop_log <- log(xy_all_cross_section$pop)
xy_all_cross_section$popdensity_log <- log(xy_all_cross_section$popdensity)
xy_all_cross_section$state_test_log <- log(xy_all_cross_section$state_test)
xy_all_cross_section$area_log <- log(xy_all_cross_section$area)
xy_all_cross_section$Median_Household_Income_2018_log <- log(xy_all_cross_section$Median_Household_Income_2018)
xy_all_cross_section$doctors_per_cap_log <- log(xy_all_cross_section$doctors_per_cap)
xy_all_cross_section$hospitals_log <- log(xy_all_cross_section$hospitals+1)

```

```{r}

temp <- xy_all_cross_section %>%
  dplyr::select(place,state, county, t_slope_percent_change,days_since_20_confirmed,pop_log,popdensity_log,state_test_percap,google_workplace,Median_Household_Income_2018,area_log,pop_over65_perc,hospitals_log) %>% 
  arrange(place)

library(GGally)
xy_all_cross_section %>%
  dplyr::select(t_slope_percent_change,days_since_20_confirmed,pop_log,popdensity_log,state_test_percap,google_workplace,Median_Household_Income_2018_log,area_log,hospitals) %>%
  ggpairs(title = "Within Psychological Variables")

```

```{r}


library(randomForestSRC); #install.packages('randomForestSRC')
rf <- rfsrc(t_slope_percent_change ~ 
              days_since_20_confirmed + 
              pop_log  + #date_numeric +
              pop_perc_male +
              pop_over65_perc + 
              pop_nonwhite_perc +
              #state_test_log +
              doctors_per_cap_log + 
              hospitals_log +
              popdensity_log +
              state_test_percap + #this is doing a ton of work
              Median_Household_Income_2018_log +
              area_log +
              google_workplace +
              google_grocery   +  google_residential + google_retail #+ google_park + google_transit
            , 
            ntree = 300 , 
            na.action='na.impute',
            data=xy_all_cross_section,
            importance="permute"
) #
rf #% variance explained: 19.6
vp <- vimp(rf)
plot(vp)

plot.variable(rf, partial = TRUE, smooth.lines = TRUE, sorted=T)

```




```{r}  
temp_df %>%
  filter(county %in% "Bexar") %>%
  ggplot() +
  geom_point(aes(x=date_asdate, y=confirmed_log)) +
  geom_line(aes(x=date_asdate, y=y_hat)) 

```

```{r}
#what should the cuttoff be?
temp_df %>% filter(confirmed<100) %>%
  ggplot() +
  geom_point(aes(x=confirmed, y=t_slope_percent_change)) 

#Where should we put the cutoff
temp_df %>% filter(confirmed<100) %>%
  ggplot(aes(x=confirmed , y=t_slope_percent_change)) +
  geom_point() +
  geom_smooth()

summary(temp_df$t_slope_percent_change[temp_df$confirmed>=10])


```

```{r}

temp_df_15 <- temp_df %>% filter(confirmed_max>10) %>% filter(days_since_15_confirmed>=1)

temp_df_15 %>% 
  ggplot(aes(x=days_since_15_confirmed , y=t_slope_percent_change)) +
  geom_point() +
  geom_smooth() + ylim(0,50)

```



```{r}
bing_long %>% filter(!is.na(death_perc_confirmed) & death_perc_confirmed!=0) %>% pull(death_perc_confirmed) %>% hist(breaks=100)
#Median of 3.7 deaths per 100
bing_long %>% filter(!is.na(death_perc_confirmed) & death_perc_confirmed!=0) %>% pull(death_perc_confirmed100) %>% summary()

bing_long$displayName

```

Without any limits we gets lots of weirdness on the low and high end. On the low end we're getting undercounting of confirmed cases. If you die, you get tested, but otherwise you're not getting reported and so the percentage of deaths is unrealistically high. On the high end the more people who are getting it, the greater share who are dying. Either because it's reaching further into communities and catching more vulnerbale people, or it's creating competition for limmitted medical resources, or both.

```{r}
bing_long %>% 
  #filter(totalDeaths>=2) %>%
  #filter(totalConfirmed>=200) %>%
  ggplot(aes(x=log(totalConfirmed),y=death_perc_confirmed100)) + geom_point() + ylim(0,50) + geom_smooth()
```

```{r}
bing_long %>% 
  filter(totalDeaths>=2) %>%
  filter(totalConfirmed>=200) %>%
  ggplot(aes(x=log(totalConfirmed),y=death_perc_confirmed100)) + geom_point() + ylim(0,25) + geom_smooth()

```



```{r}


  mutate(place=paste0(state,"_",county,"_",fips)) %>%
  group_by(place) %>%
  mutate(confirmed_cummax=cummax(confirmed)) %>%
  mutate(days_since_1_confirmed=cumsum(confirmed_cummax>=1)) %>%
  mutate(days_since_10_confirmed=cumsum(confirmed_cummax>=10)) %>%
  mutate(days_since_15_confirmed=cumsum(confirmed_cummax>=15)) %>%
  mutate(days_since_20_confirmed=cumsum(confirmed_cummax>=20)) %>%
  
  mutate(days_since_50_confirmed=cumsum(confirmed_cummax>=50)) %>%
  mutate(days_since_100_confirmed=cumsum(confirmed_cummax>=100)) %>%
  mutate(days_since_500_confirmed=cumsum(confirmed_cummax>=500)) %>%
  
  mutate(deaths_cummax=cummax(deaths)) %>%        
  mutate(days_since_1_deaths=cumsum(deaths_cummax>=1)) %>%
  mutate(days_since_10_deaths=cumsum(deaths_cummax>=10)) %>%
  mutate(days_since_50_deaths=cumsum(deaths_cummax>=50)) %>%
  mutate(days_since_100_deaths=cumsum(deaths_cummax>=100)) %>%
  mutate(days_since_500_deaths=cumsum(deaths_cummax>=500)) %>%
  
  mutate(confirmed_fd=confirmed-lag(confirmed)) %>%
  mutate(deaths_fd=deaths-lag(deaths)) %>%
  ungroup() %>%
  arrange(fips, date_asdate) %>%
  
  #filter(days_since_1_confirmed>0) %>%
  group_by(place) %>%
  mutate(confirmed_max=max(confirmed)) %>%
  ungroup() %>%
  
  mutate(deaths=ifelse(deaths==0, NA,deaths)) %>%
  mutate(confirmed=ifelse(confirmed==0, NA,confirmed)) %>%
  mutate(death_perc_confirmed= deaths / (confirmed )) %>%
  mutate(death_perc_confirmed100 = round( deaths / (confirmed/100 ),1 ) )


nytimes_long %>% filter(!is.na(death_perc_confirmed) & death_perc_confirmed!=0) %>% pull(death_perc_confirmed) %>% hist(breaks=100)
#Median of 40 deaths per 1k confirmed
nytimes_long %>% filter(!is.na(death_perc_confirmed) & death_perc_confirmed!=0) %>%  pull(death_perc_confirmed100) %>% summary()

temp <- nytimes_long %>% dplyr::select(place, confirmed, deaths, death_perc_confirmed100)

nytimes_cross <- nytimes_long %>%
  dplyr::select(state, county, fips, place, date_asdate, confirmed, deaths) %>% 
  group_by(place) %>%
  filter(date_asdate==max(date_asdate)) %>%
  ungroup() %>%
  mutate(deaths_perc_confirmed=deaths/confirmed)

temp <- nytimes_long %>% dplyr::select(fips, confirmed_max) %>% distinct()
table(temp$confirmed_max) #936 have 10 or more cases , 1412 don't

hist(nytimes_cross$deaths_perc_confirmed)

```

```{r}
%>%
                      mutate(confirmed_perc_tests= positive / (positive + negative)) %>%
                      mutate(death_perc_confirmed= death / (positive ))  %>%
                      mutate(death_perc_confirmed100 = round( death / (positive/100 ),1 ) ) %>%
                      arrange(state_name,date_asdate)

covidtracking_long %>% filter(!is.na(death_perc_confirmed) & death_perc_confirmed!=0) %>% pull(death_perc_confirmed) %>% hist(breaks=100)
#Median of 1.9 fatalities per thousand confirmed cases
covidtracking_long %>% filter(!is.na(death_perc_confirmed) & death_perc_confirmed!=0) %>% pull(death_perc_confirmed100) %>% summary()


covidtracking_cross <- covidtracking  %>% 
  
  #dplyr::select(state, county, fips, place, date_asdate, confirmed, deaths) %>% 
  group_by(state) %>%
  filter(date_asdate==max(date_asdate)) %>%
  ungroup()# %>%

```


